
## gutten 
gutten von Guttenberg’s Norway spruce (Picea abies [L.] Karst) tree measurement
data.
### Description
The data are measures from 107 trees. The trees were selected as being of average size from healthy
and well stocked stands in the Alps.
Usage
data(gutten)
### Format
A data frame with 1200 observations on the following 9 variables.
* ``site`` Growth quality class of the tree’s habitat. 5 levels.
* ``location`` Distinguishes tree location. 7 levels.
* ``tree``   An identifier for the tree within location.
* ``age.base`` The tree age taken at ground level.
* ``height`` Tree height, m.
* ``dbh.cm``: Tree diameter, cm.
* ``volume`` Tree volume.
* ``age.bh`` Tree age taken at 1.3 m.
* ``tree.ID`` A factor uniquely identifying the tree.

```{r}
data(gutten)
str(gutten)
```

### Source
The data were kindly provided to us by Professor Boris Zeide, and are documented in von Guttenberg,
A. R., 1915. Growth and yield of spruce in Hochgebirge. Franz Deuticke, Vienna (in
German).
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
Zeide, B., 1993. Analysis of growth equations. Forest Science 39 (3), 549-616
### Examples


## ``herbdata`` 
Herbicide trial seedling data

### Description
These data were collected during the 1994 planting season in Southwest Washington State.

### Usage
<pre><code>
data(herbdata)
</code></pre>

### Format
A data frame with 961 observations on the following 8 variables.
* treat treatment for control or application
* rep replication
* tree tree number in the replication
* date date the observation was made
* isalive indicator for alive/dead status
* height height of the tree in cm
* dia basal diameter of the stem, in mm
* dbh diameter at breast height, in mm
### Details
The plots were installed during the 1994 planting season in southwestern Washington by Don Wallace
and Bruce Alber. Three replications of 20 seedlings were planted in two blocks. The two
blocks were a control block and a block treated with 220 ml per hectare of Oust herbicide. The
plots were then measured over the next ten years. At each observation, the basal diameter, total
height, and condition of the stem were recorded. When the stems reached breast height (1.37 m in
the United States), the breast height diameter was also recorded. An indicator variable was used to
record if the stem was dead or alive. If the stem was dead, the observations were recorded as NA.
Source
The data are provided courtesy of Don Wallace and Bruce Alber of the Wilbur-Ellis Company.
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
### Examples
```{r}
data(herbdata)
```
