## ``generate.log.vols``

``generate.log.vols`` generates log volumes given a dataframe that contains stem measurements.

### Description

This function generates a dataframe object that contains the original stem measurements and appends columns named by ``log.grades``, where log.grades corresponds to the minimum log diameters defined by ``log.breaks``.

### Usage

<pre><code>
generate.log.vols( x,
  log.breaks=c(2,5,12,18,32,999),
  log.grades=c("pulp","s4","s3","s2","s1","peeler"),
  display.stems=FALSE )
</code></pre>

### Arguments

* ``x``: The dataframe containing the original stem measurements.
* ``log.breaks``: The vector defining the minimum diameters for the log grades defined by ``log.grades``.
* ``log.grades``: The vector defining the text labels for the ``log.breaks``.
* ``display.stems``:  The control switch to display stems as they are being merchanised.

### Details

* The function contains supporting function to determine the merchantable stem height, then talliesthe amount of Smalian log volume, in each of the ``log.grades``. 
* The resulting dataframe is then converted to be appended to each tree record in ``x``. Normally, it would not be called directly.

### Examples
```{r}
# test <- data.frame(a = c(1,2), b = c(3,4))
# show.cols.with.na(test)
# is.na(test$a[2]) <- TRUE
# show.cols.with.na(test)
```

### Value
A dataframe that contains the original stem measurements with the log volumes appended.

### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.



## ``get.col.report`` 
Obtains column information about the GLPK problem object.
### Description
This function returns a data.frame object that contains several useful column attributes about a linear
programming GLPK object.

### Usage
<pre><code>
get.col.report( lp )
</code></pre>

### Arguments
``lp`` A GLPK object.

### Details
The function generates a data.frame object that contains information from a GLPK object.

### Value
A data.frame that contains several elements returned from GLPK wrapper functions that return
attributes from a column from an GLPK object.
Author(s)
Jeff D. Hamann <jeff.hamann@forestinformatics.com>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
The GNU GLPK home page at http://www.gnu.org/software/glpk/glpk.html
### See Also
get.row.report

## ``get.row.report``
get.row.report Obtains row information about the GLPK problem object.
### Description
The function generates a data.frame object that contains row information from a GLPK object.
Usage
get.row.report( lp )
### Arguments
lp A GLPK object.
### Details
The function generates a data.frame object that contains row information from a GLPK object.
### Value
A data.frame that contains several elements returned from GLPK wrapper functions that return
attributes from a row from an GLPK object.
Author(s)
Jeff D. Hamann <jeff.hamann@forestinformatics.com>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
The GNU GLPK home page at http://www.gnu.org/software/glpk/glpk.html
### See Also
get.col.report


## ``ht.fvs.ni.m`` 
Predicts height (m) from diameter (cm) by species, using functions from Wykoff et al. (1982).

### Description
* This vectorized function uses models and parameter estimates from Wykoff et al. (1982) to predict
tree heights given over-bark diameter measurements (cm) taken at 1.37 m (4’6”). 
* The function ``ht.fvs.ni.ft`` performs the computation in imperial units, and ``ht.fvs.ni.m`` is a wrapper for convenience.

### Usage
<pre><code>
ht.fvs.ni.ft(spp, dbh.in)
ht.fvs.ni.m(spp, dbh.cm)
</code></pre>
### Arguments
* ``spp``: Tree species. Must be one of: WP, WL, DF, GF, WH, WC, LP, ES, SF, PP, MH
* ``dbh.cm``: Tree diameter, cm, measured at 1.37 m. from the ground.
* ``dbh.in``: Tree diameter, in., measured at 1.37 m. from the ground.
### Details
* The species are: WP = white pine, WL = western larch, DF = Douglas-fir, GF = grand fir, WH =
western hemlock, WC = western red cedar, LP = lodgepole pine, ES = Engelmann spruce, SF =
subalpine fir, PP = ponderosa pine, and MH = mountain hemlock.
* The function was fitted using least squares regression; the resposne variable was log of height and
the predictor variable 1 / (DBH + 1).

### Examples
```{r}
ht.fvs.ni.m(c("DF, WH"), c(25, 27))
```

### Value
The function returns a vector of tree heights, in metres.
Note
The function doesn’t perform any input checks. Caveat computator.

### References
* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
* Wykoff, W. R., Crookston, N. L., Stage, A. R., 1982. User’s Guide to the Stand Prognosis Model. GTR-INT 133, USDA Forest Service, Ogden, UT.

## leuschner 
Leuschner harvest schedule yield data
### Description
These data are used to present and study forest regulation using mathematical programming and R.
Usage
data(leuschner)
### Format
A data frame with 48 observations on the following 4 variables.

* ``stand``: index variable identifying the type of forested area
* ``period``: cutting period of the forest harvest schedule
* ``age``: at harvest at cutting period midpoint of planning period
* ``vol``: the stand volume at age, in thousands of cubic feet per acre

### Examples
```{r}
data(leuschner)
print( leuschner )
```

### Details
* This table contains example yields for an 84,000 acre (33993.93 ha) Douglas-fir forest. 
* The yields span over six (6) planning periods and eight (8) age classes from age 25 to 95 years of age.
* The data were originally published in Leuschner (1990).
### References
* Leuschner, William A. 1990. Forest Regulation, Harvest Scheduling, and Planning Techniques.
John Wiley and Sons, Inc.
* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.


## ``show.cols.with.na``
show.cols.with.na Identifies variables in a dataframe that have missing values, along
with a count.
### Description
This function reports the number of missing ### Values in each variable in a dataframe. Variables that
have no missing values are ignored.

### Usage
<pre><code>
show.cols.with.na(x)
</code></pre>

### Examples
```{r}
test <- data.frame(a = c(1,2), b = c(3,4))
show.cols.with.na(test)
is.na(test$a[2]) <- TRUE
show.cols.with.na(test)
```

### Arguments
x The dataframe to check.
### Value
A vector of missing values counts, one value for each variable with missing values. If no variables
have missing values then prints a message and exits.

### References
* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.

