---
title: "``generate.log.vols`` "
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FAwR)
```



### Description

This function generates a dataframe object that contains the original stem measurements and appends columns named by ``log.grades``, where ``log.grades`` corresponds to the minimum log diameters defined by ``log.breaks``.

### Usage

<pre><code>
generate.log.vols( x,
  log.breaks=c(2,5,12,18,32,999),
  log.grades=c("pulp","s4","s3","s2","s1","peeler"),
  display.stems=FALSE )
</code></pre>

### Arguments

* ``x``: The dataframe containing the original stem measurements.
* ``log.breaks``: The vector defining the minimum diameters for the log grades defined by ``log.grades``.
* ``log.grades``: The vector defining the text labels for the ``log.breaks``.
* ``display.stems``:  The control switch to display stems as they are being merchanised.

### Details

* The function contains supporting function to determine the merchantable stem height, then tallies the amount of Smalian log volume, in each of the ``log.grades``. 
* The resulting dataframe is then converted to be appended to each tree record in ``x``. Normally, it would not be called directly.

### Examples
```{r}
# test <- data.frame(a = c(1,2), b = c(3,4))
# show.cols.with.na(test)
# is.na(test$a[2]) <- TRUE
# show.cols.with.na(test)
```

### Value
* A dataframe that contains the original stem measurements with the log volumes appended.

### References
* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.

