---
title: "``sp.sums.2``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FAwR)
```


``sp.sums.2`` generates species summaries from a dataframe that contains stem
measurements.

### Description
This function generates a dataframe object that contains the original stem measurements and appends
columns named by ``log.grades``, where ``log.grades`` corresponds to the minimum log diameters
defined by ``log.breaks``.

### Usage

<pre><code>
sp.sums.2( x,
 log.breaks=c(2,5,12,18,32,999),
 log.grades=c("pulp","s4","s3","s2","s1","peeler") )
</code></pre>

### Arguments

* ``x``: The dataframe containing the original stem measurements.
* ``log.breaks`` The vector defining the minimum diameters for the log grades defined by ``log.grades``.
* ``log.grades`` The vector defining the text labels for the ``log.breaks``.



```{r}
 test <- data.frame(a = c(1,2), b = c(3,4))
 show.cols.with.na(test)
```
```{r}
 is.na(test$a[2]) <- TRUE
 show.cols.with.na(test)
```

### Details

The function generates summaries, by species, for common statistics used in growth and yield
simulations. It performs the same function as the ``sp.sums`` function in the ***Rconifers*** library.

### Value

A dataframe that contains the original stem measurements with the log volumes appended for each
species.

### References

* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.

