---
title: "``SSallometric`` "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FAwR)
```
## ``SSallometric`` 

Self-starting version of the allometric function $y = a x^b$.

### Description
This function is used for fitting the allometric function to bivariate data. The function is of the form
$$y = \alpha x ^{\beta},$$ where traditionally x and y are different dimensions of a sampling unit, such as
diameter and volume of a tree.

### Usage
<pre><code>
SSallometric(x, alpha, beta)
</code></pre>
### Arguments

* ``x``: predictor variable (e.g. volume)
* ``alpha``: product parameter
* ``beta``: exponent parameter

### Value

* The function returns a numeric vector of response variables. 
* The vector has two additional attributes: the gradient, which reports the first derivative of the function with respect to the parameters, evaluated at the response value; and the hessian, which reports the matrix of second partial derivatives of the function with respect to the parameters evaluated at the response variable.
* Note: Demonstrates construction and usage of self-starting functions using ``selfStart``.


### Examples
```{r}
SSallometric(10, 2, 3)
```

```{r}
data(sweetgum)
sg.model <- nls(vol.m3 ~ SSallometric(dbh.cm, alpha, beta), data = sweetgum)
sg.model
```
```{r}
summary(sg.model)
```
### References
*Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.


