---
title: "``vol.fvs.ni.m3`` "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FAwR)
```

##``vol.fvs.ni.m3`` 

Predicts volume (m^3) from diameter (cm) and height (m) by species,
using functions from Wykoff et al. (1982).

### Description

This vectorized function uses models and parameter estimates from Wykoff et al. (1982) to predict tree volumes given tree heights (m) and over-bark diameter measurements (cm) taken at 1.37 m. 
The function ``vol.fvs.ni.bdft`` performs the computation in imperial units, and ``vol.fvs.ni.m3`` is a wrapper for convenience.


### Usage
<pre><code>
vol.fvs.ni.m3(spp, dbh.cm, ht.m)
vol.fvs.ni.bdft(spp, dbh.in, ht.ft)
</code><pre>
### Arguments
* ``spp``: Tree species. Must be one of: WP, WL, DF, GF, WH, WC, LP, ES, SF, PP, MH
* ``dbh.cm``: Tree diameter, cm, measured at 1.37 m. from the ground.
* ``dbh.in``: Tree diameter, in., measured at 1.37 m. from the ground.
* ``ht.m``: Tree height, m.
* ``ht.ft``: Tree height, ft.



### Examples
```{r}
vol.fvs.ni.m3(c("DF, WH"), c(25, 27), c(15, 20))
```

### Details
The species are: WP = white pine, WL = western larch, DF = Douglas-fir, GF = grand fir, WH = western hemlock, WC = western red cedar, LP = lodgepole pine, ES = Engelmann spruce, SF = subalpine fir, PP = ponderosa pine, and MH = mountain hemlock.

### Value
The function returns a vector of tree volumes, in cubic metres.
Note
The function doesn't perform any input checks. Caveat computator.

### References
* Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
* Wykoff, W. R., Crookston, N. L., Stage, A. R., 1982. User’s Guide to the Stand Prognosis Model. GTR-INT 133, USDA Forest Service, Ogden, UT.