ddcomp: Evaluate the fit of a tree diameter distribution
==============================================================
A function to compare the fit of the observed tree diameter data (d) to a specified diameter distribution (density).


* ``d`` : numeric vector of observed diameters
* ``density`` : either a valid name for a probability density function in R or a vector of diameter 
   class densities for diameter classes whose limits are given in vector ``limitsd``.
* ``power`` : gives the weights (2 gives BA weight, 0 (default) the unweighted
* ``limits`` : the diameter class limits to compute the error index
* ``limitsd`` : see the description of argument density
* ``plot`` : logical. Should a graph be produced to illustrate the ecdf of d and the cdf corresponding to density
* ``...`` : additional arguments passed to function specified by a character-type density. e.g. Weibull 
   shape and scale of if ``density="dweibull"``
   
####  Examples

```{r}
library(lmfor)
# Example 
# Observed diameters 
d<-c(18.8,24.2,18.7,13.0,18.9,22.4,17.6,22.0,18.8,22.9,
     16.7,13.7,20.6,15.1,31.8,17.2,19.6,16.8,19.3,27.4,
	 23.7,18.2,19.7,18.9,23.0,21.4,23.8,22.1,24.2,20.9)

# Weibull(5,20) distribution in 1 cm classes (class limits from 0,...,60)
f<-pweibull(1:60,5,20)-pweibull(0:59,5,20)
```

```{r}
# compare using the classified true distribution (approximate)
ddcomp(d,density=f,limitsd=0:60,limits=0:100,plot=TRUE)

# compare b specifying a Weibull dsitribution (accurate)
ddcomp(d,density="dweibull",shape=5,scale=20,plot=TRUE)
```   
