---
title: "``bias_per``  Bias of an estimator in percentage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```


#### Description
Function for calculating the bias of an estimator.
#### Usage
bias_per(df, y, yhat)
#### Arguments 
*``df``: A data frame.
y Quoted name of the variable representing the observed values in the data frame.
If a data frame is not provided, y can also be a numeric vector.
yhat Quoted name of the variable representing the estimated values in the data frame.
If a data frame is not provided, yhat can also be a numeric vector.

#### Examples
```{r}
library(forestmangr)
data(exfm11)
head(exfm11)
# Bias of an estimator, given the data frame and quoted variable names:
bias_per(exfm11, "TH", "TH_EST3")
# Bias of an estimator, given the vectors for observed and estimated values:
bias_per(y = exfm11$TH, yhat = exfm11$TH_EST3)
```

#### Details
Function for calculating the bias of an estimator, given the observed values, and the estimated
values.
6 check_names
Value
Numeric vector with the bias value, in percentage.
Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>
See Also
other statistics to evaluate estimators: rmse_per for the Root mean square error of an estimator

