---
title: "``forestmangr::fit_clutter``:  Fit the Clutter model for growth and yield"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```
#### Description

Fit the Clutter model for growth and yield using the two stage least squares method (2SLS).

#### Usage

<pre><code>
fit_clutter(df, age, dh, basal_area, volume, site, plot, .groups = NA,
model = "full", keep_model = FALSE)
</code></pre>

#### Arguments 

* ``df``: A data frame.
* ``age``: Quoted name for the age variable.
* ``dh``: Quoted name for the dominant height variable.
* ``basal_area``: Quoted name for the basal area variable.
* ``volume``: Quoted name for the volume area variable.
* ``site``: Quoted name for the site variable.
* ``plot``:  Quoted name for the plot variable.
* ``.groups``: Optional argument. Quoted name(s) of grouping variables used to fit multiple regressions, one for each level of the provided variable(s). Default NA.
* ``model``: Character variable for the type of the model fitted. If "full", the full model will be used. if "mod", a modified model will be fitted, where the X3 variable is excluded from the regression. Default: full.
* ``keep_model``: If TRUE a variable with the regression model will be kept in the data frame. Default: FALSE.

#### Examples
```{r}
library(forestmangr)
data("exfm17")
head(exfm17)
# To fit the Clutter model we just need to define the data, and age, dominant height,
# basal area, volume, site and plot variables:
fit_clutter(exfm17, "age", "DH", "B", "V", "S", "plot")
# To fit the alternate model (without a1) just use model="mod":
fit_clutter(exfm17, "age", "DH", "B", "V", "S", "plot",model="mod")
# To keep the regression model, use keep_model=TRUE:
fit_clutter(exfm17, "age", "DH", "B", "V", "S", "plot", keep_model=TRUE)
```

#### Value
A data frame with the regressions coefficients.

#### Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>

#### References
Clutter, J. L. (1963) Compatible Growth For Loblolly by the Southeastern, Forest Science, 9(3), pp.
354–371. Sullivan, A. D. and Clutter, J. L. (1972) A Simultaneous Growth and Yield for Loblolly
Pine, Forest Science, 18(1), pp. 76–86. Campos, J. C. C. and Leite, H. G. (2017) Mensuracao
Florestal: Perguntas e Respostas. 5a. Vicosa: UFV.
See Also
other sampling functions: est_clutter for estimating the Clutter Growth and Yield model variables,
and classify_site for classifying data according to site.
