  
---
title: "``forestmangr::inv``: Calculate the inverse of a number"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```
#### Description
This function returns the inverse of a numeric vector.
#### Usage
inv(x)
#### Arguments 
x A numeric vector



#### Examples
```{r}
library(forestmangr)
data("exfm15")
head(exfm15)
# Get the inverse of a vector
inv(iris$Petal.Length)
# Fit a model that contains the inverse of a variable, without the need to
# create a new variable for the inverse:
lm(log(TH) ~ inv(DBH), exfm15 )
# or
lm_table(exfm15, log(TH) ~ inv(DBH) )


```
#### Details
This function is manly used when fitting statistical models. If one of the variables in a model is an
inverse of a vector, the lm function does not properly compute the variable, if 1/vector is inserted
directly in the model, leading to the need of creating a separate variable. This function allows the
user to get the inverse of a given numeric vector inside the model, without the need to create a new
variable.
Value
a numeric vector containing the inverse of x.
Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>
