---
title: "``pow``: pow Raise a numeric vector to a given power"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```

#### Description
This function returns a numeric vector raised to a given power.

#### Usage
<pre><code>
pow(x, y)
</code></pre>

#### Arguments 
x A numeric vector.
y A numeric value for the power x should be raised to.

#### Examples
```{r}
library(forestmangr)
data("exfm15")
head(exfm15)
# Raise a numeric vector to the power of 2:
pow(iris$Petal.Length, 2)
```
```{r}
# Fit a model that contains the dbh squared, without the need to create a new variable:
lm(log(TH) ~ DBH + pow(DBH,2), exfm15 )
# or
lm_table(exfm15, log(TH) ~ DBH + pow(DBH,2) )
```

#### Details

This function is manly used when fitting statistical models. If one of the variables in a model is a variable raised to a given power, the lm function does not properly compute the variable, if
vector^power is inserted directly in the model, leading to the need of creating a separate variable. This function allows the user to get the power of a given numeric vector to y inside the model,
without the need to create a new variable.

#### Value
a numeric vector containing x to the power of y.

#### Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>