---
title: "``resid_plot ``Calculate residual values and create plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```



#### Description
Function for creating plots and tables for residual values from observed and estimated values.
#### Usage
<pre><code>
resid_plot(df, obs, ..., type = "scatterplot", point_size = 3,
color = NA, nrow = NA, ncol = NA, lim_y = NA,
xlab = "Observed values", clab = NA, font = "serif",
legend_pos = "bottom", gray_scale = TRUE, res_table = FALSE)
</code></pre>

#### Arguments 

* ``df``: A data frame.
* ``obs``: Quoted name of the observed values variable.
* ``...``: Quoted name(s) for the estimated values variable(s). Multiple variables must be separated by comma.
* type Character object for the type of plot created, The available plots are: "scatterplot", "histogram", "histogram_curve" and "versus". Default: "scatterplot".
* ``point_size``: Numeric value for the point size in scatter plots. Default: 3.
* ``color``: Quoted name of a variable. If supplied, this variable will be used to classify the data by color. Default: NA.
* ``nrow``: Numeric value for number of rows in the plot matrix. If not supplied, the plots will be automatically sorted. Default: NA.
* ``ncol``: Numeric value for number of columns in the plot matrix. If not supplied, the plots will be automatically sorted. Default: NA.
* lim_y Numeric value for the y axis upper and lower limit. If NA, the biggest residual value is used. Default: NA.
* ``xlab``: Character value for the x label used in some plots. Default: "Observed values".
* clab Character value for the color label used, if a color variable is supplied. If not supplied, the color variable name will be used. Default: NA.
* font Type of font used in the plot. Default: "serif".
* ``legend_pos``: Position of legend, when a color variable is supplied. This can either be "left", "right", "top" or "bottom". Default: "bottom".
* gray_scale If TRUE, the plot will be rendered in a gray scale. Default: "TRUE".
* res_table If TRUE, the function will return a data frame with observed, estimated, and residual values. Default: FALSE.


#### Examples
```{r}
library(forestmangr)
data("exfm11")
head(exfm11)
# Specifying the observed and estimated variables, we get a scatter plot for the percentage residuals:
resid_plot(exfm11, "TH", "TH_EST1")
```

```{r}
# It's possible to get other types of plots, with the type argument:
resid_plot(exfm11, "TH", "TH_EST1", type = "histogram")
resid_plot(exfm11, "TH", "TH_EST1", type = "histogram_curve")
resid_plot(exfm11, "TH", "TH_EST1", type = "versus")
```

```{r}
# It's possible to add a factor variable as color in the plots:
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", color="STRATA")
# A colored plot is also available:
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", color="STRATA", gray_scale=FALSE)
# It's possible to change xlabels and color labels:
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", color="STRATA", xlab="Total Height (m)", clab="Strata")
```

```{r}
# If there are more estimated values variables, they can also be used in the comparison:
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2")
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", "TH_EST3")
```

```{r}
# It's possible to rearrange the plots with ncol and nrow:
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", "TH_EST3", ncol=1)
resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", "TH_EST3", nrow=2)
```

```{r}
# It's possible to get the residuals table used to generate these plots, with res_table=TRUE:
head( resid_plot(exfm11, "TH", "TH_EST1", "TH_EST2", res_table = TRUE) )
```

#### Value
A ggplot object, or if res_table = TRUE, a data frame.
rmse_per 49
Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>
