---
title: "``rmse_per``:   RMSE of an estimator in percentage"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```


#### Description
Function for calculating the Root-Mean-Square-Error of an estimator.

#### Usage
<pre><code>
rmse_per(df, y, yhat)
</code></pre>

#### Arguments 
*``df``: A data frame.
* y Quoted name of the variable representing the observed values in the data frame. If a data frame is not provided, y can also be a numeric vector.
* yhat Quoted name of the variable representing the estimated values in the data frame. If a data frame is not provided, yhat can also be a numeric vector.


#### Examples
```{r}
library(forestmangr)
data(exfm11)
head(exfm11)
# RMSE of an estimator, given the data frame and quoted variable names:
rmse_per(exfm11, "TH", "TH_EST3")
# RMSE of an estimator, given the vectors for observed and estimated values:
rmse_per(y = exfm11$TH, yhat = exfm11$TH_EST3)
```
#### Details
Function for calculating the Root-Mean-Square-Error of an estimator, given the observed values, and the estimated values.

#### Value
Numeric vector with the RMSE value, in percentage.

#### Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>

#### See Also
other statistics to evaluate estimators: bias_per for the bias of an estimator
