---
title: "``similarity_matrix``  Get the similarity matrix of an area"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```


#### Description
Calculates the Jaccard similarity index and Sorensen similarity index.

#### Usage
<pre><code>
similarity_matrix(df, species, comparison, NI_label = "",
index = "Sorensen")
</code></pre>

#### Arguments 
*``df``: A data frame.
* species Quoted name of the scientific names variable, or any variable used to differentiate the different species found in data. If supplied, will be used to classify the
species in the diameter data.
* comparison Quoted name of the variable containing levels to be compared with each other.
* NI_label Label used for Species not identified. This parameter works along with species. The level supplied here will not be considered in the classification. Default "".
* index Character value for the desired index to be used. Can be either Jaccard, for a matrix based on the Jaccard index of similarity, "Sorensen", for a matrix based the Sorensen index of similarity, or "all", for a list with matrices for
both indexes. Default: "Sorensen".


#### Examples
```{r}
library(forestmangr)
data(exfm20)
# To get the similarity matrix of an area, we simply need to provide
# the species variable name, and a subdivision variable name, like
# transect. By default we get a a matrix based on the Sorensen index:
similarity_matrix(exfm20, "scientific.name", "transect")
# To get the similarity matrix of Jaccard, use the index argument:
similarity_matrix(exfm20, "scientific.name", "transect", index = "Jaccard")
# To get a list with both matrices, use index="all":
similarity_matrix(exfm20, "scientific.name", "transect", index = "all")
# If the data supplied only has 2 levels, a paired comparison is made instead:
ex_pair <- exfm20[exfm20$transect %in% c("T01", "T02") , ]
ex_pair
similarity_matrix(ex_pair, "scientific.name", "transect", index = "all")
```
#### Value
a matrix object with a similarity matrix, or a list with two similarity matrices, one for each index,
according to the index argument.
Author(s)
Eric Bastos Gorgens <e.gorgens@gmail.com>
#### References
Souza, A. L. and Soares, C. P. B. (2013) Florestas Nativas: estrutura, dinamica e manejo. Vicosa:
UFV.