---
title: "``smalianwob``:  Calculate the volume without bark of trees using the Smalian method"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```



#### Description
Function used to calculate the volume without bark of trees using the Smalian method. This function
has integration with dplyr, so it can be used inside a pipe, along with the group_by function.

#### Usage
<pre><code>
smalianwob(df, di, hi, bt, tree, .groups = NA, di_mm_to_cm = FALSE,
hi_cm_to_m = FALSE, bt_mm_to_cm = FALSE)
</code></pre>

#### Arguments 

* ``df``: A data frame.
* ``di``: Quoted name of the section diameter variable, in centimeters.
* ``hi``: Quoted name of the section height variable, in meters
* ``bt``: Quoted name of the bark thickness variable, in centimeters.
* ``tree``: Quoted name of the tree variable. used to differentiate the trees’ sections. If this argument is NA, the defined groups in the data frame will be used. Default: NA.
* ``.groups``: Optional argument. Quoted name(s) of additional grouping variables that can be added to differentiate subdivisions of the data. If this argument is NA, the defined groups in the data frame will be used. Default: NA.
* ``di_mm_to_cm``: Boolean argument that, if TRUE, converts the di argument from milliliters to centimeters. Default: FALSE.
* ``hi_cm_to_m``: Boolean argument that, if TRUE, converts the hi argument from centimeters to meters. Default: FALSE.
* ``bt_mm_to_cm``: Boolean argument that, if TRUE, converts the bt argument from milliliters to centimeters. Default: FALSE.

#### Examples

```{r}
library(forestmangr)
data("exfm7")
head(exfm7)
# Calculate the volume without bark using Smalian's method:
smalianwob(exfm7,"di_wb", "hi", "bark_t", "TREE")
```

```{r}
# Using pipes:

library(dplyr)
exfm7 %>%
group_by(TREE) %>%
smalianwob("di_wb", "hi", "bark_t")
```

#### Value
Data frame with volume values by section.

#### Author(s)
Sollano Rabelo Braga <sollanorb@gmail.com>

#### References
Campos, J. C. C. and Leite, H. G. (2017) Mensuracao Florestal: Perguntas e Respostas. 5a. Vicosa:
UFV.
See Also
Complementary functions: smalianwb, For calculation of volume with bark using the Smalian
method, huberwb, for calculation of volume with bark using the Huber method, huberwob, for
calculation of volume without bark the Huber method.