---
title: "``similarity_matrix``  Get the similarity matrix of an area"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestmangr)
```

species_aggreg Get the aggregation state of species
#### Description
Get the aggregation state of species according to the Payandeh, Hazen and Morista methods.
#### Usage
<pre><code>
species_aggreg(df, species, plot, NI_label = "")
</code></pre>

#### Arguments 

* ``df``: A data frame.
* ``species``: Quoted name of the scientific names variable, or any variable used to differentiate the different species found in data.
* `` plot``:  Quoted name of the plot variable. used to differentiate the plots trees, and calculate
the number of sampled plots.
* ``NI_label``: Label used for Species not identified. This parameter works along with species. The level supplied here will not be considered in the classification. Default "".


#### Examples

```{r}
library(forestmangr)
data(exfm20)
species_aggreg(exfm20, "scientific.name", "transect")
```

#### Value
a data frame with the aggregation classification.
Author(s)
Eric Bastos Gorgens <e.gorgens@gmail.com>
#### References
Souza, A. L. and Soares, C. P. B. (2013) Florestas Nativas: estrutura, dinamica e manejo. Vicosa:
UFV.