generate.log.vols
generate.log.vols Generates log volumes given a dataframe that contains stem measurements.
### Description
This function generates a dataframe object that contains the original stem measurements and appends
columns named by log.grades, where log.grades corresponds to the minimum log diameters
defined by log.breaks.
Usage
generate.log.vols( x,
log.breaks=c(2,5,12,18,32,999),
log.grades=c("pulp","s4","s3","s2","s1","peeler"),
display.stems=FALSE )
### Arguments
x The dataframe containing the original stem measurements.
* ``log.breaks`` The vector defining the minimum diameters for the log grades defined by log.grades.
* ``log.grades`` The vector defining the text labels for the log.breaks.
* ``display.stems``  The control switch to display stems as they are being merchanised.
### Details
The function contains supporting function to determine the merchantable stem height, then tallies
the amount of Smalian log volume, in each of the log.grades. The resulting dataframe is then
converted to be appended to each tree record in x. Normally, it would not be called directly.
### Value
A dataframe that contains the original stem measurements with the log volumes appended.
Author(s)
Jeff D. Hamann <jeff.hamann@forestinformatics.com>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
### See Also
is.na
get.col.report 3
### Examples
# test <- data.frame(a = c(1,2), b = c(3,4))
# show.cols.with.na(test)
# is.na(test$a[2]) <- TRUE
# show.cols.with.na(test)
get.col.report Obtains column information about the GLPK problem object.
### Description
This function returns a data.frame object that contains several useful column attributes about a linear
programming GLPK object.
Usage
get.col.report( lp )
### Arguments
lp A GLPK object.
### Details
The function generates a data.frame object that contains information from a GLPK object.
### Value
A data.frame that contains several elements returned from GLPK wrapper functions that return
attributes from a column from an GLPK object.
Author(s)
Jeff D. Hamann <jeff.hamann@forestinformatics.com>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
The GNU GLPK home page at http://www.gnu.org/software/glpk/glpk.html
### See Also
get.row.report

## ``get.row.report``
get.row.report Obtains row information about the GLPK problem object.
### Description
The function generates a data.frame object that contains row information from a GLPK object.
Usage
get.row.report( lp )
### Arguments
lp A GLPK object.
### Details
The function generates a data.frame object that contains row information from a GLPK object.
### Value
A data.frame that contains several elements returned from GLPK wrapper functions that return
attributes from a row from an GLPK object.
Author(s)
Jeff D. Hamann <jeff.hamann@forestinformatics.com>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
The GNU GLPK home page at http://www.gnu.org/software/glpk/glpk.html
### See Also
get.col.report


## ht.fvs.ni.m 
Predicts height (m) from diameter (cm) by species, using functions from Wykoff et al. (1982).
### Description
This vectorized function uses models and parameter estimates from Wykoff et al. (1982) to predict
tree heights given over-bark diameter measurements (cm) taken at 1.37 m (4’6”). The function
ht.fvs.ni.ft performs the computation in imperial units, and ht.fvs.ni.m is a wrapper for convenience.
### Usage
<pre><code>
ht.fvs.ni.ft(spp, dbh.in)
ht.fvs.ni.m(spp, dbh.cm)
</code></pre>
### Arguments
* ``spp``: Tree species. Must be one of: WP, WL, DF, GF, WH, WC, LP, ES, SF, PP, MH
* ``dbh.cm``: Tree diameter, cm, measured at 1.37 m. from the ground.
* ``dbh.in``: Tree diameter, in., measured at 1.37 m. from the ground.
### Details
The species are: WP = white pine, WL = western larch, DF = Douglas-fir, GF = grand fir, WH =
western hemlock, WC = western red cedar, LP = lodgepole pine, ES = Engelmann spruce, SF =
subalpine fir, PP = ponderosa pine, and MH = mountain hemlock.
The function was fitted using least squares regression; the resposne variable was log of height and
the predictor variable 1 / (DBH + 1).
### Value
The function returns a vector of tree heights, in metres.
Note
The function doesn’t perform any input checks. Caveat computator.
Author(s)
Andrew Robinson <apro@unimelb.edu.au>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
Wykoff, W. R., Crookston, N. L., Stage, A. R., 1982. User’s Guide to the Stand Prognosis Model.
GTR-INT 133, USDA Forest Service, Ogden, UT.
8 leuschner

### Examples
```{r}
ht.fvs.ni.m(c("DF, WH"), c(25, 27))
```
## leuschner 
Leuschner harvest schedule yield data
### Description
These data are used to present and study forest regulation using mathematical programming and R.
Usage
data(leuschner)
### Format
A data frame with 48 observations on the following 4 variables.

* ``stand``: index variable identifying the type of forested area
* ``period``: cutting period of the forest harvest schedule
* ``age``: at harvest at cutting period midpoint of planning period
* ``vol``: the stand volume at age, in thousands of cubic feet per acre
### Details
This table contains example yields for an 84,000 acre (33993.93 ha) Douglas-fir forest. The yields
span over six (6) planning periods and eight (8) age classes from age 25 to 95 years of age.
Source
The data were originally published in Leuschner (1990).
### References
Leuschner, William A. 1990. Forest Regulation, Harvest Scheduling, and Planning Techniques.
John Wiley and Sons, Inc.
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
### Examples
```{r}
data(leuschner)
print( leuschner )
```

## ``show.cols.with.na``
show.cols.with.na Identifies variables in a dataframe that have missing ### Values, along
with a count.
### Description
This function reports the number of missing ### Values in each variable in a dataframe. Variables that
have no missing ### Values are ignored.
Usage
show.cols.with.na(x)
### Arguments
x The dataframe to check.
### Value
A vector of missing ### Values counts, one ### Value for each variable with missing ### Values. If no variables
have missing ### Values then prints a message and exits.
Author(s)
Andrew Robinson <apro@unimelb.edu.au>
### References
Robinson, A.P., and J.D. Hamann. 2010. Forest Analytics with R: an Introduction. Springer.
### See Also
is.na
### Examples
```{r}
test <- data.frame(a = c(1,2), b = c(3,4))
show.cols.with.na(test)
is.na(test$a[2]) <- TRUE
show.cols.with.na(test)
```
