---
title: "FI::volume "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(FI)
```


## volume
Estimates the stem volume

##### Description
volume uses one of the following methods (Smalian, Newton, Huber) to approximate real stem
volume. Users should remember they’re just approximations and sample size provide more accurate
results them using different methods.

#### Usage
<pre><code>
volume(trees, method = "smalian")
</code></pre>

#### Arguments
* trees a data frame or matrix in format described in dataset inventory (more help inventory)
* method method used for estimation of the stem volume


#### Examples

```{r}
example_data <- data.frame(tree_number = 1,
dhb = 5,
total_height = 20,
comercial_height = 15,
section_height = c(0,5,15),
section_diameter = 5
)volume
volume(example_data)
#
#
# A little more complex and common example
data(inventory)
volume_output <- volume(inventory)
summary(volume_output)
hist(volume_output)
```
##### Value
a named vector of volumes, names are defined as same as in first column

#### Note
Newton and Huber methods have small modifications for working just with two mensures (lower and upper diameter). Both of them use mean instead of real middle diameter.

##### References
http://wiki.awf.forst.uni-goettingen.de/wiki/index.php/Stem_volume
See Also
ff sf

