## monomolecular Monomolecular growth model

#### Description
Computes the monomolecular growth model
\[y(t) = (1 ?? exp(??kt))\]

### Usage 
<pre><code>
monomolecular(t, alpha, beta, k)
monomolecular.inverse(x, alpha, beta, k)
</code></pre>

### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate

### Examples
```{r}
growth <- monomolecular(0:10, 10, 0.5, 0.3)
# Calculate inverse function
time <- monomolecular.inverse(growth, 10, 0.5, 0.3)
``

### References
* D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.
`

## ``negativeExponential`` Negative exponential growth model

#### Description
Computes the negative exponential growth model
\[y(t) = (1 ?? exp(??kt))\]

### Examples
```{r}
growth <- negativeExponential(0:10, 1, 0.3)
# Calculate inverse function
time <- negativeExponential.inverse(growth, 10, 0.3)
```

### Usage 
<pre><code>
negativeExponential(t, alpha, k)
negativeExponential.inverse(x, alpha, k)
</code><pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``k``: growth rate


### References
* D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.


## ``richard`` Richard growth model

### Description
Computes the Richard growth model and its inverse
\[y(t) = (1 + exp(??kt))(1=m)\]
### Usage 
<pre><code>
richard(t, alpha, beta, k, m)
richard.inverse(x, alpha, beta, k, m)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate
*``m``: slope of growth

### Examples
```{r}
growth <- richard(0:10, 10, 0.5, 0.3, 0.5)
time <- richard.inverse(growth, 10, 0.5, 0.3, 0.5)
```

### References
* D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.

## ``schnute`` Schnute growth model

#### Description
Computes the Schnute growth model
\[y(t) = [r0 + exp(kt)]m\]

### Usage 
<pre><code>
schnute(t, r0, beta, k, m)
schnute.inverse(x, r0, beta, k, m)
</code></pre>

### Arguments 
*``t``: time
*``x``: size
*``r0``: reference value
*``beta``: growth displacement
*``k``: growth rate
* ``m``: slope of growth

### References
A. Khamiz, Z. Ismail, and A. T. Muhammad, "Nonlinear growth models for modeling oil palm yield
growth," Journal of Mathematics and Statistics, vol. 1, no. 3, p. 225, 2005.
### Examples
```{r}
growth <- schnute(0:10, 10, 5, .5, .5)
# Calculate inverse function
time <- schnute.inverse(growth, 10, 5, .5, .5)
```
