## ``blumberg`` Blumberg growth model

#### Description
Computes the Blumberg growth model and its inverse

\[y(t) =   (t + t0)m w0 + (t + t0)m\]

### Usage 

<pre><code>
blumberg(t, alpha, w0, m, t0 = 0)
blumberg.inverse(x, alpha, w0, m, t0 = 0)
</code></pre>

### Arguments 
* ``t``: time
* ``x``: size
* ``alpha``: upper asymptote
* ``w0``: a reference value at t = t0
* ``m``: slope of growth
* ``t0``: time shift (default 0)

### References
* A. Tsoularis and J. Wallace, "Analysis of logistic growth models.," Math Biosci, vol. 179, no. 1,
pp. 21-55, Jul. 2002.

### Examples
```{r}
growth <- blumberg(0:10, 10, 2, 0.5)
# Calculate inverse function
time <- blumberg.inverse(growth, 12, 2, 0.5)
```

## ``brody`` Brody growth model

#### Description
Computes the Brody growth model and its inverse
\[ y(t) =  ?? ( ?? w0)exp(??kt)\]

### Usage 
<pre><code>
brody(t, alpha, w0, k)
brody.inverse(x, alpha, w0, k)
</code></pre>

### Examples
```{r}
growth <- brody(0:10, 10, 5, 0.3)
# Calculate inverse function
time <- brody.inverse(growth, 10, 5, 0.3)
```

### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``w0``: the value at t = 0
*``k``: growth rate

### References
* M. M. Kaps, W. O. W. Herring, and W. R. W. Lamberson, "Genetic and environmental parameters
for traits derived from the Brody growth curve and their relationships with weaning weight in Angus
cattle.," Journal of Animal Science, vol. 78, no. 6, pp. 1436-1442, May 2000.

