## stannard Stannard growth model

#### Description
Computes the Stannard growth model
\[ y(t) =  [1 + exp(??( + kt)=m)]??m \]

### Usage 
<pre><code>
stannard(t, alpha, beta, k, m)
stannard.inverse(x, alpha, beta, k, m)
</code></pre>

### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth displacement
*``k``: growth rate
*``m``: slope of growth

### Examples
```{r}
growth <- stannard(0:10, 1, .2, .1, .5)
# Calculate inverse function
time <- stannard.inverse(growth, 1, .2, .1, .5)
```
### References
* A. Khamiz, Z. Ismail, and A. T. Muhammad, "Nonlinear growth models for modeling oil palm yield
growth," Journal of Mathematics and Statistics, vol. 1, no. 3, p. 225, 2005.


## ``vonBertalanffy`` von Bertalanffy growth model

#### Description
Computes the von Bertalanffy growth model
\[y(t) = ((1 ?? m) ??   exp(??kt))(1=(1 ?? m))\]

### Usage 
<pre><code>
vonBertalanffy(t, alpha, beta, k, m)
vonBertalanffy.inverse(x, alpha, beta, k, m)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate
*``m``: slope of growth

### Examples
```{r}
growth <- vonBertalanffy(0:10, 10, 0.5, 0.3, 0.5)
# Calculate inverse function
time <- vonBertalanffy.inverse(growth, 10, 0.5, 0.3, 0.5)
```
### References
* D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.

## ``weibull`` Weibull growth model

#### Description
Computes the Weibull growth model
\[y(t) =  ?? exp(??k  tm)\]

### Usage 
<pre><code>
weibull(t, alpha, beta, k, m)
weibull.inverse(x, alpha, beta, k, m)
</code><pre>

### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate
*``m``: slope of growth

### Examples
```{r}
growth <- weibull(0:10, 10, 0.5, 0.3, 0.5)
# Calculate inverse function
time <- weibull.inverse(growth, 10, 0.5, 0.3, 0.5)
```

### References
D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.
