generalisedRichard Generalised Richard growth model
Description
Computes the Generalised Richard growth model and its inverse
y(t) = A +
U ?? A
(1 + exp(??k(t ?? t0)))(1=m)
### Usage 
<pre><code>
generalisedRichard(t, A, U, k, m, beta, t0)
generalisedRichard.inverse(x, A, U, k, m, beta, t0 = 0)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
A the lower asymptote
U the upper asymptote
k growth range
m slope of growth
*``beta``: growth range
t0 time shift (default 0)
gompertz 7
### References
http://en.wikipedia.org/wiki/Generalised_logistic_function
### Examples
```{r}
growth <- generalisedRichard(0:10, 5, 10, 0.3, 0.5, 1, 3)
time <- generalisedRichard.inverse(growth, 5, 10, 0.3, 0.5, 1, 3)
```

## gompertz Gompertz growth model

###Description
Computes the Gompertz growth model and its inverse
y(t) = exp(??exp(??kt))
### Usage 
<pre><code>
gompertz(t, alpha, beta, k)
gompertz.inverse(x, alpha, beta, k)
```
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth displacement
*``k``: growth rate

### Examples
growth <- gompertz(0:10, 10, 0.5, 0.3)
# Calculate inverse function
time <- gompertz.inverse(growth, 10, 0.5, 0.3)
### References
D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.

## ``logistic`` Logistic growth model

#### Description
Computes the Logistic growth model
y(t) =

1 + exp(??kt)
### Usage 
<pre><code>
logistic(t, alpha, beta, k)
logistic.inverse(x, alpha, beta, k)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate
### References
D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.
### Examples
```{r}
growth <- logistic(0:10, 10, 0.5, 0.3)
# Calculate inverse function
time <- logistic.inverse(growth, 10, 0.5, 0.3)
```

## ``loglogistic`` Log-logistic growth model

#### Description: Computes the Log-logistic growth model
\[y(t) = 1 + exp(??klog(t)\]

### Usage 
<pre><code>
loglogistic(t, alpha, beta, k)
loglogistic.inverse(x, alpha, beta, k)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate
### References
A. Khamiz, Z. Ismail, and A. T. Muhammad, "Nonlinear growth models for modeling oil palm yield
growth," Journal of Mathematics and Statistics, vol. 1, no. 3, p. 225, 2005.
### Examples
growth <- loglogistic(0:10, 10, 0.5, 0.3)
# Calculate inverse function
time <- loglogistic.inverse(growth, 10, 0.5, 0.3)

## ``mitcherlich`` Mitcherlich growth model

#### Description
Computes the Mitcherlich growth model
\[y(t) = ( ?? kt)\]

### Usage 
<pre><code>
0mitcherlich(t, alpha, beta, k)
mitcherlich.inverse(x, alpha, beta, k)
</code></pre>

### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
*``beta``: growth range
*``k``: growth rate

### References
D. Fekedulegn, M. Mac Siurtain, and J. Colbert, "Parameter estimation of nonlinear growth models
in forestry," Silva Fennica, vol. 33, no. 4, pp. 327-336, 1999.
### Examples
```{r}
growth <- mitcherlich(0:10, 10, 0.5, 0.3)
# Calculate inverse function
time <- mitcherlich.inverse(growth, 10, 0.5, 0.3)
```
## ``mmf`` Morgan-Mercer-Flodin growth model

#### Description
Computes the Morgan-Mercer-Flodin growth model
\[y(t) = (w0 + tm) + tm \]

### Usage 
<pre><code>
mmf(t, alpha, w0, gamma, m)
mmf.inverse(x, alpha, w0, gamma, m)
</code></pre>
### Arguments 
*``t``: time
*``x``: size
*``alpha``: upper asymptote
w0 the value at t = 0
gamma parameter that controls the point of inflection
m growth rate
### References
A. Khamiz, Z. Ismail, and A. T. Muhammad, "Nonlinear growth models for modeling oil palm yield
growth," Journal of Mathematics and Statistics, vol. 1, no. 3, p. 225, 2005.
### Examples
```{r}
growth <- mmf(0:10, 10, 0.5, 4, 1)
# Calculate inverse function
time <- mmf.inverse(growth, 10, 0.5, 4, 1)
```
