---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

DBH Trees height and diameter at breast height

#### Description

The DBH data contains the diameter at breast height (dbh), height and condition data for all trees
centered in 108 plots of size 0.2 hectare immediately following a single prescribed burn and also
following three 5-yr (year) interval reburns (four burns total) and a single 15-yr interval reburn
(two burns total) and associated treatment information. The trees information were established
from mixed ponderosa pine (Pinus ponderosa Dougl. ex Laws.) that contained scattered western
junipers (Juniperus occidentalis Hook.). The plots were located in the Malheur National Forest on
the southern end of the Blue Mountains near Burns, Oregon, USA.

#### Usage

data(DBH)
Format
A text file with 5732 observations from 17 variables related of trees characteristics such as dbh and
height.

dgsm 

#### Description

Computes probability density function (pdf) of the gamma shape mixture (GSM) model. The general
form for the pdf of the GSM model is given by
f(x; \Theta ) =
XK
j=1
\omega_{j}
\betaj
????(j)
xj????1 exp
????
????\betax

;
where $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant K is the number of
components. The vector of mixing parameters is given by ! = (\omega_{1}, \ldots, \omega_{K})T where \omega_{j}s sum to
one, i.e.,
PK
j=1 \omega_{j} = 1. Here \beta is the rate parameter that is equal for all components.

#### Usage

dgsm(data, omega, beta, log = FALSE)

#### Arguments

* ``data``:   Vector of observations.
omega Vector of the mixing parameters.
beta The rate parameter.
log If TRUE, then log(pdf) is returned.

#### Value

A vector of the same length as data, giving the pdf of the GSM model.
### Author(s)
Mahdi Teimouri
4 dmixture



#### Examples
```{r}

data<-seq(0,20,0.1)
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-2
dgsm(data, omega, beta)

