---
title: "``ForestFit::dgsm``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```


#### Description

Computes probability density function (pdf) of the gamma shape mixture (GSM) model. The general
form for the pdf of the GSM model is given by
\[f(x; \Theta ) = \sum_{j=1}^{K}\omega_{j} \frac{\beta^{j}}{\Gamma(j)} x^{j-1} exp(-\beta x);\]
where $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant $K$ is the number of
components. 

The vector of mixing parameters is given by $\omega = (\omega_{1}, \ldots, \omega_{K})^T where $\omega_{j}s$ sum to
one, i.e.,
\[ \sum^{K}_{j=1} \omega_{j} = 1.\] Here $\beta$ is the rate parameter that is equal for all components.

#### Usage

<pre><code>
dgsm(data, omega, beta, log = FALSE)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``omega``: Vector of the mixing parameters.
* ``beta``: The rate parameter.
* ``log``: If TRUE, then log(pdf) is returned.



#### Examples
```{r}
library(magrittr)

data<-seq(0,20,0.1)
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-2
dgsm(data, omega, beta) %>% head(20)

```

```{r}
plot( dgsm(data, omega, beta), type = "l" )

```


#### Value

A vector of the same length as data, giving the pdf of the GSM model.

### Author(s)
Mahdi Teimouri
