---
title: "ForestFit::dmixture"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

Computing probability density function of the well-known mixture models

#### Description

* Computes probability density function (pdf) of the mixture model. General form for the cdf of a statistical mixture model is given by
\[F(x; \Theta ) =  \sum^{K}_{j=1}
\omega_{j}F_j(x; \theta j);\]
where $\Theta  = (\theta 1, \ldots, \theta_K)^T$ , is the whole parameter vector, $\theta_j$ for $ j = 1, \ldots,K$ is the parameter
space of the j-th component, i.e. $\theta_j = (\alpha_j ; \beta_j)^T$ , $F_j( \cdot , \theta_j)$ is the cdf of the j-th component, and
known constant $K$ is the number of components. 
* Parameters $\alpha$ and $\beta$ are the shape and scale parameters or both are the shape parameters. 
* In the latter case, the parameters $\alpha$ and $\beta$ are called
the first and second shape parameters, respectively. 
* We note that the constants $\omega_{j}$s sum to one,
i.e.
\[ \sum^{K}_{j=1} \omega_{j} \;=\; 1 \]

#### Families

The families considered for the cdf F include Birnbaum-Saunders, Burr type XII, Chen, F, Frechet, Gamma, Gompertz, Log-normal, Log-logistic, Lomax, skew-normal, and Weibull.


#### Usage

<pre><code>
dmixture(data, g, K, param)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``g``:  Name of the family including "birnbaum-saunders", "burrxii", "chen", "f", "Frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax", "skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the $\omega$, $\alpha$, $\beta$, and $\lambda$.



#### Examples
```{r}

data<-seq(0,20,0.1)
K<-2
weight<-c(0.6,0.4)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
dmixture(data, "weibull", K, param)
```

```{r}
plot(dmixture(data, "weibull", K, param) ,type="l" )
```

```{r}
plot(dmixture(data, "birnbaum-saunders", K, param) ,type="l" )
```

#### Details

For the skew-normal case, $\alpha$, $\beta$, and $\lambda$  are the location, scale, and skewness parameters, respectively.


#### Value

A vector of the same length as data, giving the pdf of the mixture model of families computed at data.

### Author(s)
Mahdi Teimouri
