---
title: "ForestFit::dmixture"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

Computing probability density function of the well-known mixture models

#### Description

Computes probability density function (pdf) of the mixture model. General form for the cdf of a statistical mixture model is given by
\[F(x; \Theta ) =  \sum^{K}_{j=1}
\omega_{j}F_j(x; \theta j);\]
where $\Theta  = (\theta 1, \ldots, \theta_K)^T$ , is the whole parameter vector, $\theta_j$ for $ j = 1, \ldots,K$ is the parameter
space of the j-th component, i.e. $\theta_j = (\alpha_j ; \beta_j)^T$ , $F_j( \cdot , \theta_j)$ is the cdf of the j-th component, and
known constant $K$ is the number of components. Parameters $\alpha$ and $\beta$ are the shape and scale
parameters or both are the shape parameters. In the latter case, the parameters $\alpha$ and $\beta$ are called
the first and second shape parameters, respectively. 
We note that the constants $\omega_{j}$s sum to one,
i.e.
\[ \sum^{K}_{j=1} \omega_{j} \;=\; 1 \]

The families considered for the cdf F include Birnbaum-Saunders, Burr type
XII, Chen, F, Frechet, Gamma, Gompertz, Log-normal, Log-logistic, Lomax, skew-normal, and
Weibull, with pdf given by the following.
. Birnbaum-Saunders
f(x; \theta ) =
q
x
\beta +
q
\beta
x
2\alpha\;x

 q
x
\beta ????
q
\beta
x
\alpha\;
!
;
. Burr XII
f(x; \theta ) = \alpha\;\betax\alpha\;????1

1 + x\alpha\;
????\beta????1
;
. Chen
f(x; \theta ) = \alpha\;\betax\alpha\; exp
????
x\alpha\;
exp
n
????\beta exp
????
x\alpha\;
+ \beta
o
;
. F
f(x; \theta ) =
????

\alpha\;+\beta
2

????
????\alpha\;
2

????
???? \beta
2

\alpha\;
\beta
\alpha\;
2
x
\alpha\;
2 ????1

1 +
\alpha\;
\beta
x
????\alpha\;+\beta
2
;
dmixture 5
. Frechet
f(x; \theta ) =
\alpha\;
\beta
x
\beta
????\alpha\;????1
exp
n
????
x
\beta
????\alpha\;o
;
. gamma
f(x; \theta ) =
\Theta 
\beta\alpha\;????(\alpha\;)
????1
x\alpha\;????1 exp

????
x
\beta

;
. Gompertz
f(x; \theta ) = \beta exp
????
\alpha\;x

exp
(
\beta exp
????
\alpha\;x

???? 1
\alpha\;
)
;
. log-logistic
f(x; \theta ) =
\alpha\;
\beta\alpha\; x\alpha\;????1
x
\beta
\alpha\;
+ 1
\lambda ????2
;
. log-normal
f(x; \theta ) =
????p
2\betax
????1
exp

????
1
2
\theta 
log x ???? \alpha\;
\beta
2
;
. Lomax
f(x; \theta ) =
\alpha\;\beta
(1 + \alpha\;x)\beta+1 ;
. skew-normal
f(x; \theta ) = 2
x ???? \alpha\;
\beta

\Psi

\lambda 
x ???? \alpha\;
\beta

;
. Weibull
f(x; \theta ) =
\alpha\;
\beta
x
\beta
\alpha\;????1
exp
n
????
x
\beta
\alpha\;o
;
where \theta  = (\alpha\;; \beta). In the skew-normal case, (:) and \Psi(:) are the density and distribution functions
of the standard normal distribution, respectively.

#### Usage

<pre><code>
dmixture(data, g, K, param)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``g``:  Name of the family including "birnbaum-saunders", "burrxii", "chen", "f", "Frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax", "skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the !, \alpha\;, \beta, and \lambda .



#### Examples
```{r}

data<-seq(0,20,0.1)
K<-2
weight<-c(0.6,0.4)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
dmixture(data, "weibull", K, param)
```


#### Details

For the skew-normal case, $\alpha$, $\beta$, and $\lambda$  are the location, scale, and skewness parameters, respectively.


#### Value

A vector of the same length as data, giving the pdf of the mixture model of families computed at data.

### Author(s)
Mahdi Teimouri
