---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitbayesJSB Estimating parameters of the Johnson's SB (JSB) distribution using
the Bayesian approach

#### Description

Suppose $x = (x1, \ldots, xn)^T$ denotes a vector of n independent observations coming from a fourparameter
JSB distribution with pdf given by
f
????
x
\beta\beta
\Theta 

=
\delta \; \lambda 
p
2(x ???? \upsilon \; )(\lambda  + \upsilon \;  ???? x)
exp
(
????
1
2
"

 + \delta \;  log
\theta 
x ???? \upsilon \; 
\lambda  + \upsilon \;  ???? x
#2)
;
where \upsilon \;  < x < \lambda  + \upsilon \;  and \Theta  = (\delta \; ; 
; \lambda ; \upsilon \; )T with \delta \; ; \lambda  > 0, ????1 < 
 < 1, and ????1 < \upsilon \;  < 1.
Using the Bayesian approach, we compute the Bayes' estimators of the JSB distribution parameters.

#### Usage

fitbayesJSB(data, n.burn=8000, n.simul=10000)

#### Arguments

* ``data``:   Vector of observations.
n.burn Length of the burn-in period, i.e., the point after which Gibbs sampler is supposed
to attain convergence. By default n.burn is 8000.
n.simul Total numbers of Gibbas sampler iterations. By default n.simul is 10,000.

#### Details

The Bayes' estimators are obtained by averaging on the all iterations between n.burn and n.simul.
fitbayesWeibull 7

#### Value

A list of objects in two parts as
1. Bayes' estimators of the parameters.
2. A sequence of four goodness-of-fit measures consist of Anderson-Darling (AD), Cram\'eer-von
Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.

### Author(s)
Mahdi Teimouri



#### Examples
```{r}

n<-20
xi<-0
delta<-2
gamma<-2
lambda<-20
z<-rnorm(n)
data<-xi+lambda/(1+exp(-(z-gamma)/delta))
fitbayesJSB(data, n.burn=50, n.simul=80)
```
