---
title: "``ForestFit::fitbayesWeibull``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

Estimating parameters of the Weibull distribution using the Bayesian approach

#### Description

Suppose $x = (x^1, \ldots, x^n)^T$ denotes a vector of n independent observations coming from a threeparameter
Weibull distribution. Using the methodology given in Green et al. (1994), we compute
the Bayes' estimators of the shape, scale, and location parameters.

#### Usage

<pre><code>
fitbayesWeibull(data, n.burn=8000, n.simul=10000)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``n.burn``: Length of the burn-in period, i.e., the point after which Gibbs sampler is supposed to attain convergence. By default ``n.burn`` is 8000.
* ``n.simul``: Total numbers of Gibbas sampler iterations. By default ``n.simul`` is 10,000.




#### Examples
```{r}

n<-20
alpha<-2
beta<-2
theta<-3
set.seed(1234); mydata<-rweibull(n,shape=alpha,scale=beta)+theta
fitbayesWeibull(mydata, n.burn=100, n.simul=200)
```

#### Details

The Bayes' estimators are obtained by averaging on the all iterations between ``n.burn`` and ``n.simul``.

#### Value

A list of objects in two parts as
1. Bayes' estimators of the parameters.
2. A sequence of four goodness-of-fit measures consist of Anderson-Darling (AD), Cram\'eer-von
Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.

### Note

The methodology used here for computing the Bayes' estimator of the location parameter is different
from that used by Green et al. (1994). This means that the location parameter is allowed to be
any real value.

### Author(s)
Mahdi Teimouri
