---
title: "``ForestFit::fitbayesJSB``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

 Estimating parameters of the Johnson's SB (JSB) distribution using
the Bayesian approach

#### Description

Suppose $x = (x^1, \ldots, x^n)^T$ denotes a vector of $n$ independent observations coming from a four parameter
JSB distribution with pdf given by


\[
f(x|\Theta )
=
\frac{\delta \lambda}{\sqrt{2\pi}(x -\xi)(\lambda + \xi -x )} exp\left\{ -\frac{1}{2} \left[ \gamma + \delta \log \left( \frac{x -\xi}{\lambda + \xi -x } \right) \right]^2  \right\}\]

where $\xi \;  < x < \lambda  + \xi \;$  and $\Theta  = (\delta \; ; 
; \lambda ; \xi \; )^T$ with $\delta \; ; \lambda  > 0, -\infty < 
 < \infty, $ and $ -\infty  < \xi \;  < \infty $
 
Using the Bayesian approach, we compute the Bayes' estimators of the JSB distribution parameters.

#### Usage

<pre><code>
fitbayesJSB(data, n.burn=8000, n.simul=10000)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``n.burn``: Length of the burn-in period, i.e., the point after which Gibbs sampler is supposed to attain convergence. By default ``n.burn`` is 8000.
* ``n.simul``: Total numbers of Gibbas sampler iterations. By default n.simul is 10,000.

#### Examples

```{r}

n<-20
xi<-0
delta<-2
gamma<-2
lambda<-20
z<-rnorm(n)
mydata<-xi+lambda/(1+exp(-(z-gamma)/delta))
fitbayesJSB(mydata, n.burn=50, n.simul=80)
```

#### Details

The Bayes' estimators are obtained by averaging on the all iterations between ``n.burn`` and ``n.simul``.

#### Value

A list of objects in two parts as
1. Bayes' estimators of the parameters.
2. A sequence of four goodness-of-fit measures consist of Anderson-Darling (AD), Cramer-von Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.

### Author(s)
Mahdi Teimouri
