---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitgsm Estimating parameters of the gamma shape mixture model

#### Description

Estimates parameters of the gamma shape mixture (GSM) model whose probability density function
gets the form as follows.
f(x; \Theta ) =
XK
j=1
\omega_{j}
\betaj
????(j)
xj????1 exp
????
????\betax

;
fitgsm 13
where $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant K is the number of
components. The vector of mixing parameters is given by ! = (\omega_{1}, \ldots, \omega_{K})T where \omega_{j}s sum to
one, i.e.,
PK
j=1 \omega_{j} = 1. Here \beta is the rate parameter that is equal for all components.

#### Usage

fitgsm(data,K)

#### Arguments

* ``data``:   Vector of observations.
* `` K``:    Number of components.

#### Details

Supposing that the number of components, i.e., K is known, the parameters are estimated through
the EM algorithm developed by the maintainer.

#### Value

A list of objects in three parts as
1. The EM estimator of the rate parameter.
2. The EM estimator of the mixing parameters.
3. A sequence of goodness-of-fit measures consist of Akaike Information Criterion (AIC), Consistent
Akaike Information Criterion (CAIC), Bayesian Information Criterion (BIC), Hannan-
Quinn information criterion (HQIC), Anderson-Darling (AD), Cram\'eer-von Misses (CVM), Kolmogorov-
Smirnov (KS), and log-likelihood (log-likelihood) statistics.
### Author(s)
Mahdi Teimouri


#### Examples
```{r}

n<-100
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-2
data<-rgsm(n,omega,beta)
K<-length(omega)
fitgsm(data,K)
```
