---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitgrowth 

Estimatinng the parametersof the fitted non-linear growth curve to the height-diameter(H-D) observations

#### Description

Estimates the parameters of the nine well-known three-parameter non-linear curves fitted to the
height-diameter observations. These nine models are given by the following.
. Richards (Richards(1959))
H = 1:3 + \beta1 +
\beta2
D + \beta3
;
. Gompertz (Winsor(1992))
H = 1:3 + \beta1e????\beta2e????\beta3D
;
fitgrowth 11
. Hossfeld IV (Zeide(1993))
H = 1:3 +
\beta1
1 + 1
\beta2D\beta3
;
. Korf (Flewelling and De Jong(1994))
H = 1:3 + \beta1e????\beta2D????\beta3 ;
. logistic (Pearl and Reed (1920))
H = 1:3 +
\beta1
1 + \beta2e????\beta3D ;
. Prodan (Prodan(1968))
H = 1:3 +
D2
\beta1D2 + \beta2D + \beta3
;
. Ratkowsky (Ratkowsky(1990))
H = 1:3 + \beta1e???? \beta2
D+\beta3 ;
. Sibbesen (Huang et al. (1992))
H = 1:3 + \beta1D\beta2D????\beta3 ;
. Weibull (Yang et al. (1978))
H = 1:3 + \beta1

1 ???? e????\beta2D\beta3

;

#### Usage

fitgrowth(h,d,model,starts)

#### Arguments

* ``h``: Vector of height observations.
d Vector of diameter observations.
model The name of the fitted model including "chapman-richards", "gompertz",
"hossfeldiv", "korf", "logistic", "prodan" , "ratkowsky", "Sibbesen", and
"weibull".
starts A list of starting values for the parameters \beta1, \beta2, and \beta3.

#### Value

A list of objects in four parts as
1. Estimated parameters and corresponding summaries including standard errors, computed t-
statistics, and p-values.
2. Residuals.
3. Covariance matrix of the estimated model parameters (coefficients) ^ \beta1, ^ \beta2, and ^ \beta3.
4. Residual standard error, i.e., ^.
5. The hieght-diameter scatterplot superimposed by the fitted model.
12 fitgsm
### Author(s)
Mahdi Teimouri



#### Examples
```{r}

# use the heigth and diameter at breast height (dbh) of the plot 55 in DBH data set.
# The first column of DBH dataset contains the plot number. Also, H and D denote the
# height and dbh variables that located at columns 10 and 11 of data set DBH, respectively.
data(DBH)
D<-DBH[DBH[,1]==55,10]
H<-DBH[DBH[,1]==55,11]
starts<-c(9,0.0005,2)
fitgrowth(H,D,"weibull",starts=starts)
