---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitgrouped Estimating parameters of the three-parameter Birnbaum-saunders
(BS), generalized exponential (GE), and Weibull distributions fitted to
grouped data

#### Description

Suppose a sample of n independent observations each follows a three-parameter BS, GE, orWeibull
distributions have been divided into m separate groups of the form (ri????1; ri], for i = 1, \ldots,m. So,
the likelihood function is given by
L(\Theta ) =
n!
f1!f2! : : : fm!
mY
i=1
h
F
????
ri
\beta\beta
\Theta 

???? F
????
ri????1
\beta\beta
\Theta 
ifi
;
fitgrouped 9
where the r0 is the lower bound of the first group, rm is the upper bound of the last group, and
fi is the frequency of observations within i-th group provided that n =
Pm
i=1 fi. The cdf of a
three-parameter BS, GE, and Weibull distributions are given by
F(x; \Theta ) =
\theta 
1 ???? exp
\Psi
????\beta(x ???? )
	\alpha\;
;
F(x; \Theta ) = \Psi
 q
x
\beta ????
q
\beta
x
\alpha\;
!
;
and
F(x; \Theta ) = 1 ???? exp
n
????
\theta 
x ???? 
\beta
\alpha\;o
;
where \Theta  = (\alpha\;; \beta; )T .

#### Usage

<pre><code>
fitgrouped(r, f, family, method1, starts, method2)
</code></pre>

#### Arguments

* ``r``: A numeric vector of length m + 1. The first element of r is lower bound of the
first group and other m elements are upper bound of the m groups. We note that
upper bound of the (i ???? 1)-th group is the lower bound of the i-th group, for
i = 2, \ldots,m. The lower bound of the first group and upper bound of the m-th group are chosen arbitrarily.
* ``f``: A numeric vector of length m containing the group's frequency.
family Can be either "birnbaum-saunders", "ge", or "weibull".
method1 A character string determining the method of estimation. It can be one of "aml",
"em" and "ml". The short forms "aml", "em", and "ml" are described as follows.
""aml" (for method of approximated maximum likelihood (aml)), ""em" (for method of expectation maximization (em)), and ""ml" (for method of maximum
likelihood (ml)).
starts A numeric vector of the initial values for the shape, scale, and location parameters, respectively.
method2 The method for optimizing the log-likelihood function. It invovles one of "BFGS",
"Nelder-Mead", "CG", "L-BFGS-B" or "SANN".

#### Details

If the method is "em", then the initial values ("starts") and the log-likelihood optimizing method ("method2") are ignored.

#### Value

A two-part list of objects given by the following:
1. Estimated parameters of the three-parameter GE, Birnbaum-Saunders, or Weibull distribution
fitted to the gropued data.
2. A sequence of goodness-of-fit measures consist of Akaike Information Criterion (AIC), Consistent
Akaike Information Criterion (CAIC), Bayesian Information Criterion (BIC), Hannan-
Quinn information criterion (HQIC), Anderson-Darling (AD), Chi-square (Chi-square), Cram\'eervon
Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.
### Author(s)
Mahdi Teimouri



#### Examples
```{r}

r<-c(0,1,2,3,4,10)
f<-c(2,8,12,15,4)
starts<-c(2,2,0)
fitgrouped(r,f,"birnbaum-saunders","em")
fitgrouped(r,f,"weibull","ml",starts,"CG")
fitgrouped(r,f,"ge","em")
```

