---
title: "``ForestFit::fitgsm``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

Estimating parameters of the gamma shape mixture model

#### Description

Estimates parameters of the gamma shape mixture (GSM) model whose probability density function
gets the form as follows.

\[f(x; \Theta ) = \sum_{j=1}^{K}\omega_{j} \frac{\beta^{j}}{\Gamma(j)} x^{j-1} exp(\-beta x);\]
where $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant $K$ is the number of
components. The vector of mixing parameters is given by $\omega = (\omega_{1}, \ldots, \omega_{K})^T$ where $\omega_{j}s$ sum to
one, i.e.,
\[ \sum^{K}_{j=1} \omega_{j} = 1.\] Here $\beta$ is the rate parameter that is equal for all components.

#### Usage
<pre><code>
fitgsm(data,K)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* `` K``:    Number of components.

#### Details

Supposing that the number of components, i.e., $K$ is known, the parameters are estimated through
the EM algorithm developed by the maintainer.




#### Examples
```{r}

n<-1000
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-3
data<-rgsm(n,omega,beta)
K<-length(omega)
fitgsm(data,K)
```

```{r}
fittedmodel.beta <-fitgsm(data,K)$`beta`
fittedmodel.omega <-fitgsm(data,K)$omega


```


#### Value

A list of objects in three parts as
1. The EM estimator of the rate parameter.
2. The EM estimator of the mixing parameters.
3. A sequence of goodness-of-fit measures consist of Akaike Information Criterion (AIC), Consistent Akaike Information Criterion (CAIC), Bayesian Information Criterion (BIC), Hannan-Quinn information criterion (HQIC), Anderson-Darling (AD), Cramer-von Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.

### Author(s)
Mahdi Teimouri
