---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitmixturegrouped Estimating parameters of the well-known mixture models fitted to the
grouped data

#### Description

Estimates parameters of the gamma, log-normal, and Weibull mixture models fitted to the grouped
data using the expectation maximization (EM) algorithm. General form for the cdf of a statistical
mixture model is given by
F(x; \Theta ) =
XK
k=1
\omega_{K}Fk(x; \theta k);
16 fitmixturegrouped
where \Theta  = (\theta 1, \ldots, \theta K)T , is the whole parameter vector, \theta k for k = 1, \ldots,K is the parameter
space of the j-th component, i.e. \theta k = (\alpha\;k; \betak)T , Fj(:; \theta j) is the cdf of the k-th component,
and known constant K is the number of components. Parameters $\alpha$ and $\beta$ are the shape and scale
parameters. The constants \omega_{K}s sum to one, i.e.
PK
k=1 \omega_{K} = 1. The families considered for the
cdf F include Gamma, Log-normal, and Weibull. If a sample of n independent observations each
follows a distribution with cdf F have been divided into m separate groups of the form (ri????1; ri],
for i = 1, \ldots,m. So, the likelihood function of the observed data is given by
L(\Theta jf1, \ldots, fm) =
n!
f1!f2! : : : fm!
mY
i=1
hFi(\Theta )
F(\Theta )
ifi
;
where
Fi(\Theta ) =
XK
k=1
\omega_{K}
Z ri
ri????1
f(xj\theta k)dx;
F(\Theta ) =
XK
k=1
\omega_{K}f(xj\theta k)dx;
in which f(xj\theta k) denotes the pdf of the j-th component. Using the the EM algorithm proposed by
Dempster et al. (1977), we can solve @L(\Theta jf1, \ldots, fm)=@\Theta  = 0 by introducing two new missing
variables.

#### Usage

fitmixturegrouped(family, r, f, K, initial=FALSE, starts)

#### Arguments

* ``family```: Name of the family including: "gamma", "log-normal", "skew-normal", and
"weibull".
* ``r``: A numeric vector of length m + 1. The first element of r is lower bound of the
first group and other m elements are upper bound of the m groups. We note that
upper bound of the (i ???? 1)-th group is the lower bound of the i-th group, for
i = 2, \ldots,m. The lower bound of the first group and upper bound of the m-th
group are chosen arbitrarily. If raw data are available, the smallest and largest
observations are chosen for lower bound of the first group and upper bound of
the m-th group, respectively.
* ``f``: A numeric vector of length m containing the group's frequency.
* `` K``:    Number of components.
initial The sequence of initial values including \omega_{1}, \ldots, \omega_{K}; \alpha\;1, \ldots, \alpha\;K; \beta1, \ldots, \betaK.
For skew normal case the vector of initial values of skewness parameters will
be added. By default the initial values automatically is determind by k-means
method of clustering.
starts If initial=TRUE, then sequence of the initial values must be given.

#### Details

Identifiability of the mixture models supposed to be held. For skew-normal mixture model the
parameter vector of k-th component gets the form \theta k = (\alpha\;k; \betak; \lambda k)T where \alpha\;k; \betak; and \lambda k denote
the location, scale, and skewness parameters, respectively.
fitWeibull 17

#### Value

1. The output has two parts, The first part includes vector of estimated weight, shape, and scale
parameters.
2. A sequence of goodness-of-fit measures consist of Akaike Information Criterion (AIC), Consistent
Akaike Information Criterion (CAIC), Bayesian Information Criterion (BIC), Hannan-
Quinn information criterion (HQIC), Anderson-Darling (AD), Cram\'eer-von Misses (CVM), Kolmogorov-
Smirnov (KS), and log-likelihood (log-likelihood) statistics.
### Author(s)
Mahdi Teimouri


#### Examples
```{r}

n<-50
K<-2
m<-10
weight<-c(0.3,0.7)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
data<-rmixture(n, "weibull", K, param)
r<-seq(min(data),max(data),length=m+1)
D<-data.frame(table(cut(data,r,labels=NULL,include.lowest=TRUE,right=FALSE,dig.lab=4)))
f<-D$Freq
fitmixturegrouped("weibull",r,f,K,initial=FALSE)
```