---
title: "``ForestFit::fitmixture``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

fitmixture Estimating parameters of the well-known mixture models

#### Description

Estimates parameters of the mixture model using the expectation maximization (EM) algorithm.
General form for the cdf of a statistical mixture model is given by
\[F(x; \Theta ) =
XK
j=1
\omega_{j}Fj(x; \theta j);\]
where \Theta  = (\theta 1, \ldots, \theta K)T , is the whole parameter vector, \theta j for $ j = 1, \ldots,K$ is the parameter
space of the j-th component, i.e. $\theta j = (\alpha\;j ; \betaj)T$ , $Fj(:; \theta j)$ is the cdf of the j-th component, and
known constant K is the number of components. Parameters $\alpha$ and $\beta$ are the shape and scale
parameters or both are the shape parameters. In the latter case, the parameters $\alpha$ and $\beta$ are called
the first and second shape parameters, respectively. We note that the constants \omega_{j}s sum to one,
i.e.
PK
j=1 \omega_{j} = 1. The families considered for the cdf F include Birnbaum-Saunders, Burr type
XII, Chen, F, Frechet, Gamma, Gompertz, Log-normal, Log-logistic, Lomax, skew-normal, and
Weibull.

#### Usage

fitmixture(data, family, K, initial=FALSE, starts)

#### Arguments

* ``data``:   Vector of observations.
* ``family```: Name of the family including: "birnbaum-saunders", "burrxii", "chen", "f",
"Frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax",
"skew-normal", and "weibull".
* `` K``:    Number of components.
initial The sequence of initial values including \omega_{1}, \ldots, \omega_{K}; \alpha\;1, \ldots, \alpha\;K; \beta1, \ldots, \betaK.
For skew normal case the vector of initial values of skewness parameters will
be added. By default the initial values automatically is determind by k-means
method of clustering.
starts If initial=TRUE, then sequence of the initial values must be given.

#### Details

It is worth noting that identifiability of the mixture models supposed to be held. For skew-normal
case we have \theta j = (\alpha\;j ; \betaj ; \lambda j)T in which ????1 < \alpha\;j < 1, \betaj > 0, and ????1 < \lambda j < 1,
respectively, are the location, scale, and skewness parameters of the j-th component, see Azzalini
(1985).
fitmixturegrouped 15

#### Value

1. The output has three parts, The first part includes vector of estimated weight, shape, and scale
parameters.
2. The second part involves a sequence of goodness-of-fit measures consist of Akaike Information
Criterion (AIC), Consistent Akaike Information Criterion (CAIC), Bayesian Information
Criterion (BIC), Hannan-Quinn information criterion (HQIC), Anderson-Darling (AD), Cram\'eervon
Misses (CVM), Kolmogorov-Smirnov (KS), and log-likelihood (log-likelihood) statistics.
3. The last part of the output contains clustering vector.
### Author(s)
Mahdi Teimouri



#### Examples
```{r}

n<-50
K<-2
m<-10
weight<-c(0.3,0.7)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
data<-rmixture(n, "weibull", K, param)
fitmixture(data,"weibull", K, initial=FALSE)
```