---
title: "Untitled"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


pgsm Computing cumulative distribution function of the gamma shape mixture
model

#### Description

Computes cumulative distribution function (cdf) of the gamma shape mixture (GSM) model. The
general form for the cdf of the GSM model is given by


\[ F(X,\Theta) \;=\; \sum_{j=1}^{K}\omega_{j}F(X,j,\beta)\]

where


\[F(X,j,\beta) \;=\; \int^{x}_{0} \frac{\beta^{j}}{\Gamma(j)} y^{j-1} exp(-\beta y) dy \]
in which $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant K is the number of
components. The vector of mixing parameters is given by $\omega = (\omega_{1}, \ldots, \omega_{K})^T where $\omega_{j}s$ sum to
one, i.e.,
\[ \sum^{K}_{j=1} \omega_{j} = 1.\] Here $\beta$ is the rate parameter that is equal for all components.


#### Usage

<pre><code>
pgsm(data, omega, beta, log.p = FALSE, lower.tail = TRUE)
</code></pre>
 
#### Arguments

* ``data``:   Vector of observations.
omega Vector of the mixing parameters.
beta The rate parameter.
log.p If TRUE, then log(cdf) is returned.
lower.tail If FALSE, then 1-cdf is returned.

#### Value

A vector of the same length as data, giving the cdf of the GSM model.
### Author(s)
Mahdi Teimouri


#### Examples
```{r}

data<-seq(0,20,0.1)
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-2
pgsm(data, omega, beta)
```

