---
title: "``ForestFit::pmixture`` "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```


Computing cumulative distribution function of the well-known mixture models

#### Description

Computes cumulative distribution function (cdf) of the mixture model. The general form for the cdf of a statistical mixture model is given by
\[F(x; \Theta ) =  \sum^{K}_{j=1}
\omega_{j}F_j(x; \theta j);\]
where $\Theta  = (\theta 1, \ldots, \theta_K)^T$ , is the whole parameter vector, $\theta_j$ for $ j = 1, \ldots,K$ is the parameter space of the j-th component, i.e. $\theta_j = (\alpha_j ; \beta_j)^T$ , $F_j( \cdot , \theta_j)$ is the cdf of the j-th component, and known constant $K$ is the number of components.

The vector of mixing parameters is given
by \[ ! = (\omega_{1}, \ldots, \omega_{K})^T\] where $\omega_{j}$s sum to one, i.e.,
\[ \sum^{K}_{j=1} \omega_{j} \;=\; 1 \]


Parameters $\alpha$ and $\beta$ are the shape and scale
parameters or both are the shape parameters. In the latter case, the parameters $\alpha$ and $\beta$ are called the first and second shape parameters, respectively.

#### Families

The families considered for each component include Birnbaum-Saunders, Burr type XII, Chen, F, Frechet, Gamma, Gompertz,
Log-normal, Log-logistic, Lomax, skew-normal, and Weibull.

#### Usage
<pre><code>
pmixture(data, g, K, param)
</code></pre>

#### Arguments

* ``data``:   Vector of observations.
* ``g``:  Name of the family including: "birnbaum-saunders", "burrxii", "chen", "f", "frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax",
"skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the $\omega$, $\alpha$, $\beta$, and $\lambda$  .

#### Details

For the skew-normal case, $\alpha$, $\beta$, and $\lambda$  are the location, scale, and skewness parameters, respectively.

#### Value

A vector of the same length as data, giving the cdf of the mixture model computed at data.

#### Examples

```{r}
data<-seq(0,20,0.1)
K<-2
weight<-c(0.6,0.4)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
pmixture(data, "weibull", K, param)
```


```{r}
plot( pmixture(data, "weibull", K, param),type="l" )

```