---
title: "ForestFit::pmixture "
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```


Computing cumulative distribution function of the well-known mixture
models

#### Description

Computes cumulative distribution function (cdf) of the mixture model. The general form for the cdf
of the mixture model is given by
\[F(x; \Theta ) =
XK
j=1
\omega_{j}F(x; \theta j);\]
where $\Theta  = (\theta 1, \ldots, \theta K)^T$ , is the whole parameter vector, \theta j for $ j = 1, \ldots,K$ is the parameter
space of the j-th component, i.e. \theta j = (\alpha\;j ; \betaj)T , Fj(:; \theta j) is the cdf of the j-th component,
and known constant K is the number of components. 

The vector of mixing parameters is given
by ! = (\omega_{1}, \ldots, \omega_{K})T where \omega_{j}s sum to one, i.e.,
PK
j=1 \omega_{j} = 1. Parameters $\alpha$ and $\beta$ are the
shape and scale parameters or both are the shape parameters. 

In the latter case, the parameters \alpha\;
and $\beta$ are called the first and second shape parameters, respectively. The families considered for
each component include Birnbaum-Saunders, Burr type XII, Chen, F, Frechet, Gamma, Gompertz,
Log-normal, Log-logistic, Lomax, skew-normal, and Weibull.

#### Usage

pmixture(data, g, K, param)

#### Arguments

* ``data``:   Vector of observations.
* ``g``:  Name of the family including: "birnbaum-saunders", "burrxii", "chen", "f", "frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax",
"skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the !, \alpha\;, \beta, and \lambda .

#### Details

For the skew-normal case, \alpha\;, \beta, and \lambda  are the location, scale, and skewness parameters, respectively.

#### Value

A vector of the same length as data, giving the cdf of the mixture model computed at data.

#### Examples

```{r}
data<-seq(0,20,0.1)
K<-2
weight<-c(0.6,0.4)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
pmixture(data, "weibull", K, param)
```