---
title: "rgsm"
author: "Kevin O Brien"
date: "28 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

rgsm Simulating realizations from the gamma shape mixture model

#### Description

Simulates realizations from a gamma shape mixture (GSM) model with probability density function
given by
\[f(x; \Theta ) =
XK
j=1
\omega_{j}
\beta j
????(j)
xj????1 exp
????
????\ta be  tax

;\]
where $\Theta  = (\omega_{1}, \ldots, \omega_{K}; \beta)^T$ is the parameter vector and known constant K is the number of
components. The vector of mixing parameters is given by ! = (\omega_{1}, \ldots, \omega_{K})T where $\omega_{j}s$ sum to
one, i.e.,
\[ \sum^{K}_{j=1} \omega_{j} = 1.\] Here $\beta$ is the rate parameter that is equal for all components.

#### Usage

<pre><code>
rgsm(n, omega, beta)
</code></pre>

#### Arguments

* n Vector of observations.
* omega Vector of the mixing parameters.
* beta The rate parameter.

#### Value

A vector of length n, giving random generated values from GSM model.

### Author(s)

Mahdi Teimouri



#### Examples
```{r}

n<-100
omega<-c(0.05, 0.1, 0.15, 0.2, 0.25, 0.25)
beta<-2
rgsm(n, omega, beta)