---
title: "``ForestFit::rmixture``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

 Generating random realizations from the well-known mixture models

#### Description

Generates iid realizations from the mixture model with pdf given by
\[f(x; ) =
XK
j=1
!jf(x; j);
\]
where K is the number of components, j , for j = 1; : : : ;K is parameter space of the j-th component,
i.e. j = (j ; j)T , and  is the whole parameter vector  = (1; : : : ; K)T . Parameters
 and  are the shape and scale parameters or both are the shape parameters. 
 
 In the latter
case, parameters  and  are called the first and second shape parameters, respectively. We note
that the constants !js sum to one, i.e.,
PK
j=1 !j = 1. The families considered for the cdf f
include Birnbaum-Saunders, Burr type XII, Chen, F, Fr\'echet, Gamma, Gompertz, Log-normal,
Log-logistic, Lomax, skew-normal, and Weibull.

#### Usage

rmixture(n, g, K, param)

#### Arguments

* ``n``: Number of requested random realizations.
* ``g``:  Name of the family including "birnbaum-saunders", "burrxii", "chen", "f",
"frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax",
"skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the !, , , and .

#### Details

For the skew-normal case, , , and  are the location, scale, and skewness parameters, respectively.

#### Value

A vector of length n, giving a sequence of random realizations from given mixture model.

#### Examples
```{r}

n<-50
K<-2
weight<-c(0.3,0.7)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
rmixture(n, "weibull", K, param)
```