---
title: "``ForestFit::rmixture``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ForestFit)
```

Generating random realizations from the well-known mixture models

#### Description

Generates iid realizations from the mixture model with pdf given by
\[f(x; \theta ) =  \sum^{K}_{j=1} \omega_{j}f_j(x; \theta j);\]
where K is the number of components, $\theta_j$ for $ j = 1, \ldots,K$ is the parameter space of the j-th component, i.e. $theta_j = (\alpha_j ; \beta_j)^T$ , and $\Theta  = (\theta_1, \ldots, \theta_K)^T$ , is the whole parameter vector. 

Parameters $\alpha$ and $\beta$ are the shape and scale parameters or both are the shape parameters. 
In the latter case, the parameters $\alpha$ and $\beta$ are called the first and second shape parameters, respectively. We note that the constants $\omega_{j}$s sum to one, i.e.
\[ \sum^{K}_{j=1} \omega_{j} \;=\; 1 \]

#### Families

The families considered for the cdf F include Birnbaum-Saunders, Burr type XII, Chen, F, Frechet, Gamma, Gompertz, Log-normal, Log-logistic, Lomax, skew-normal, and Weibull

#### Usage

<pre><code>
rmixture(n, g, K, param)
</code></pre>

#### Arguments

* ``n``: Number of requested random realizations.
* ``g``:  Name of the family including "birnbaum-saunders", "burrxii", "chen", "f", "frechet", "gamma", "gompetrz", "log-normal", "log-logistic", "lomax",
"skew-normal", and "weibull".
* `` K``:    Number of components.
* `` param ``:    Vector of the $\omega$, $\alpha$, $\beta$, and $\lambda$  .


#### Examples
```{r}

n<-5000
K<-2
weight<-c(0.3,0.7)
alpha<-c(1,2)
beta<-c(2,1)
param<-c(weight,alpha,beta)
set.seed(1234); 
MyMixture<- data.frame(
  component1 = rmixture(n, "weibull", 1, c(1,1,2)),
  component2 = rmixture(n, "weibull", 1, c(1,2,1)),
  mixture = rmixture(n, "weibull", K, param))
```

```{r}

library(ggplot2)

ggplot() + 
  geom_density(data=MyMixture,aes(x=component1),colour="red") + 
  geom_density(data=MyMixture,aes(x=component2),colour="red") + 
  geom_density(data=MyMixture,aes(x=mixture),lwd=1.0) + 
  theme_bw() + 
  geom_hline(yintercept = 0) + geom_vline(xintercept = 0)

```

#### Details

For the skew-normal case, $\alpha$, $\beta$, and $\lambda$  are the location, scale, and skewness parameters, respectively.


#### Value

A vector of length n, giving a sequence of random realizations from given mixture model.