tidy
Transforming a rWind_series object into a data.frame
#### Description

The output of tidy is always a data.frame. It is therefore suited for further manipulation by packages
like dplyr, reshape2, ggplot2 and ggvis.6
uv2ds
Usage
tidy(x, ...)
## S3 method for class 'rWind_series'
tidy(x, ...)
Arguments
x An object to be converted into a tidy data.frame
... extra arguments
#### Examples
 ```{r}
data(wind.series)
df <- tidy(wind.series)
head(df)
## Not run:
# use the tidyverse
library(dplyr)
mean_speed <- tidy(wind.series) %>% group_by(lat, lon) %>%
summarise(speed=mean(speed))
wind_average2 <- wind.mean(wind.series)
all.equal(wind_average2$speed, mean_speed$speed)
## End(Not run)
uv2ds
Transform U and V components in direction and speed and vice versa
#### Description

Transform U and V components in direction and speed and vice versa
Usage
uv2ds(u, v)
ds2uv(d, s)
Arguments
u U component.
v U component.
d direction (degrees).
s speed (m/s).wind.data
7
#### Value

"uv2ds" returns a matrix with direction and speed values
"ds2uv" returns a matrix with U and V values
Note
Multiple U and V values can be procesed.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)
See Also
wind.mean, wind2raster
#### Examples
 ```{r}
( ds <- uv2ds(c(1,1,3,1), c(1,1.7,3,1)) )
ds2uv(ds[,1], ds[,2])
