wind.data
Wind data example
#### Description

This is an example of wind data obtained with wind.dl function for the Iberian Peninsula coorde-
nates on 12/February/2015 at 00:00 (UTC)
Format
A list with one data.frame with 651 observations on the following 7 variables:
list("time (UTC)") a numeric with selected time of wind data
list("latitude (degrees_north)") a numeric with latitude values
list("longitude (degrees_east)") a numeric with longitude values
list("ugrd10m (m s-1)") a numeric with U component of wind data
list("vgrd10m (m s-1)") a numeric with V component of wind data
list("dir") a numeric with direction of wind data
list("speed") a numeric with speed of wind data8
wind.dl
#### Details 
 
This data set is the result of:
wind.data <- wind.dl(2015,2,12,0,-10,5,35,45)
Source
http://allthiswasfield.blogspot.com.es/2016/12/rwind-r-package-released.html

#### References 
 
http://oos.soest.hawaii.edu/erddap/info/NCEP_Global_Best/index.html
#### Examples
 ```{r}
data(wind.data)
str(wind.data)
head(wind.data[[1]])
wind.dl
Wind-data download
#### Description

wind.dl downloads wind data from the Global Forecast System (GFS) of the USA’s National Weather
Service (NWS) (https://www.ncdc.noaa.gov/data-access/model-data/model-datasets/global-forcast-
system-gfs). Wind data are taken from NOAA/NCEP Global Forecast System (GFS) Atmospheric
Model colection. Geospatial resolution is 0.5 degrees (approximately 50 km), and wind is calculated
for Earth surface, at 10 m. More metadata information: http://oos.soest.hawaii.edu/erddap/info/NCEP_Global_Best/index.htm
Usage
wind.dl(yyyy, mm, dd, tt, lon1, lon2, lat1, lat2, type = "read-data",
trace = 1)
read.rWind(file)
Arguments
yyyy Selected year.
mm Selected month.
dd Selected day.
tt Selected time. There are currently several options at the GFS database: 00:00 -
03:00 - 06:00 - 09:00 - 12:00 - 15:00 - 18:00 - 21:00 (UTC).
lon1 Western longitudewind.dl
9
lon2 Eastern longitude
lat1 Southern latitude
lat2 Northern latitude
type Output type. "read-data" is selected by default, creating an R object. If you
choose "csv", wind.dl create a a CSV file in your working directory named
"wind_yyyy_mm_dd_tt.csv".
trace if trace = 1 (by default) track downloaded files
file file name of the saved ".csv" files.
#### Details 
 
The output type is determined by type="csv" or type="read-data". If type="csv" is selected, the
function creates a "wind_yyyy_mm_dd_tt.csv" file that is downloaded at the work directory. If
type="read-data" is selected, an R object (data.frame) is created.
#### Value

"rWind" and "data.frame" class object or .csv file with U and V vector components and wind direc-
tion and speed for each coordenate in the study area defined by lon1/lon2 and lat1/lat2.
Note
Longitude coordenates are provided by GFS dataset in 0/360 notation and transformed internaly
into -180/180.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)

#### References 
 
http://www.digital-geography.com/cloud-gis-getting-weather-data/#.WDOWmbV1DCL
http://oos.soest.hawaii.edu/erddap/griddap/NCEP_Global_Best.graph
See Also
wind.dl_2, wind2raster
#### Examples
 ```{r}
# Download wind for Iberian Peninsula region at 2015, February 12, 00:00
## Not run:
wind.dl(2015,2,12,0,-10,5,35,45)
## End(Not run)
```

wind.dl_2
