
wind.mean
Wind-data mean
#### Description

wind.mean computes the mean (average) wind speed and wind direction of a time series dataset
of winds of the same region. Summaries of time series are not trivial to compute. We com-
pute the arithmetic mean for the wind speed. The direction as the circular mean, see https:
//en.wikipedia.org/wiki/Mean_of_circular_quantities for more details. The U and V
componenats are afterwards transformed from these values.12
wind.series
Usage
wind.mean(x)
Arguments
x
An object of class rWind_series
#### Value

An object of class rWind, which is a data.frame
Note
For large time series, it could take a while.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)

#### References 
 
https://en.wikipedia.org/wiki/Cross_product
See Also
wind.dl
#### Examples
 ```{r}
data(wind.series)
wind_average<- wind.mean(wind.series)
wind.series
Wind series example
#### Description

This is an example of a wind series data obtained with wind.dl function for New Zealand area on
3/January/2015 at all the available times: 00:00 - 03:00 - 06:00 - 09:00 - 12:00 - 15:00 - 18:00 -
21:00 (UTC)wind2raster
13
Format
The format is an rWind list of 8 data.frame. Each data.frame contain 961 observations on the
following 7 variables:
list("time (UTC)") a factor with selected time of wind data
list("latitude (degrees_north)") a factor with latitude values
list("longitude (degrees_east)") a factor with longitude values
list("ugrd10m (m s-1)") a factor with U component of wind data
list("vgrd10m (m s-1)") a factor with V component of wind data
list("dir") a numeric with direction of wind data
list("speed") a numeric with speed of wind data
#### Details 
 
This data set is the result of:
library(lubridate) dt <- seq(ymd_h(paste(2015,1,3,00, sep="-")),
wind.series <- wind.dl_2(dt, 164, 179, -48, -33)
ymd_h(paste(2015,1,3,21, sep=
Source
http://allthiswasfield.blogspot.com.es/2016/12/rwind-r-package-released.html

#### References 
 
http://oos.soest.hawaii.edu/erddap/info/NCEP_Global_Best/index.html
#### Examples
 ```{r}
data(wind.series)
str(tidy(wind.series))
