Wind-data download
#### Description

wind.dl_2 downloads time-series wind data from the Global Forecast System (GFS) of the USA’s
National Weather Service (NWS) (https://www.ncdc.noaa.gov/data-access/model-data/model-datasets/global-
forcast-system-gfs). Wind data are taken from NOAA/NCEP Global Forecast System (GFS) Atmo-
spheric Model colection. Geospatial resolution is 0.5 degrees (approximately 50 km), and wind is
calculated for Earth surface, at 10 m. More metadata information: http://oos.soest.hawaii.edu/erddap/info/NCEP_Global_Bes
Usage
wind.dl_2(time, lon1, lon2, lat1, lat2, type = "read-data", trace = 1)
## S3 method for class 'rWind_series'
x[[i, exact = TRUE]]
Arguments
time
lon1
lon2
lat1
lat2
type
trace
x
i
exact
a scalar or vector of POSIXt or Date objects or an character which can transfored
into those, see example below. There are currently these options at the GFS
database for the hours: 00:00 - 03:00 - 06:00 - 09:00 - 12:00 - 15:00 - 18:00 -
21:00 (UTC) (TO).
Western longitude
Eastern longitude
Southern latitude
Northern latitude
Output type. "read-data" is selected by default, creating an R object. If you
choose "csv", wind.dl create a a CSV file in your work directory named "wind_yyyy_mm_dd_tt.csv".
if trace = 1 (by default) track downloaded files
object from which to extract element(s).
indices specifying elements to extract.
Controls possible partial matching (not used yet).
#### Details 
 
To get the same format as wind.dl, you should run tidy function from wind.dl_2 output. The output
type is determined by type="csv" or type="read-data". If type="csv" is selected, the function creates
a "wind_yyyy_mm_dd_tt.csv" file that is downloaded at the work directory. If type="read-data" is
selected, an rWind_series object is created.
#### Value

an object of class rWind_series or .csv file/s with U and V vector components and wind direction
and speed for each coordenate in the study area defined by lon1/lon2 and lat1/lat2.wind.mean
11
Note
wind.dl_2 requires two dates that represent the boundaries of the time lapse to download wind
series data. U and V vector components allow you to create wind averages or tendences for each
coordenate at the study area. Longitude coordenates are provided by GFS dataset in 0/360 notation
and transformed internaly into -180/180.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)

#### References 
 
http://www.digital-geography.com/cloud-gis-getting-weather-data/#.WDOWmbV1DCL
http://oos.soest.hawaii.edu/erddap/griddap/NCEP_Global_Best.graph
See Also
wind.mean, wind2raster, wind.dl, as_datetime, as.POSIXct
#### Examples
 ```{r}
# Download wind for Iberian Peninsula region at 2015, February 12, 00:00
## Not run:
wind.dl_2("2018/3/15 9:00:00",-10,5,35,45)
library(lubridate)
dt <- seq(ymd_hms(paste(2018,1,1,00,00,00, sep="-")),
ymd_hms(paste(2018,1,2,21,00,00, sep="-")),by="3 hours")
ww <- wind.dl_2(dt,-10,5,35,45)
tidy (ww)
## End(Not run)
wind.mean
Wind-data mean
#### Description

wind.mean computes the mean (average) wind speed and wind direction of a time series dataset
of winds of the same region. Summaries of time series are not trivial to compute. We com-
pute the arithmetic mean for the wind speed. The direction as the circular mean, see https:
//en.wikipedia.org/wiki/Mean_of_circular_quantities for more details. The U and V
componenats are afterwards transformed from these values.12
wind.series
Usage
wind.mean(x)
Arguments
x
An object of class rWind_series
#### Value

An object of class rWind, which is a data.frame
Note
For large time series, it could take a while.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)

#### References 
 
https://en.wikipedia.org/wiki/Cross_product
See Also
wind.dl
#### Examples
 ```{r}
data(wind.series)
wind_average<- wind.mean(wind.series)
wind.series
Wind series example
#### Description

This is an example of a wind series data obtained with wind.dl function for New Zealand area on
3/January/2015 at all the available times: 00:00 - 03:00 - 06:00 - 09:00 - 12:00 - 15:00 - 18:00 -
21:00 (UTC)wind2raster
13
Format
The format is an rWind list of 8 data.frame. Each data.frame contain 961 observations on the
following 7 variables:
list("time (UTC)") a factor with selected time of wind data
list("latitude (degrees_north)") a factor with latitude values
list("longitude (degrees_east)") a factor with longitude values
list("ugrd10m (m s-1)") a factor with U component of wind data
list("vgrd10m (m s-1)") a factor with V component of wind data
list("dir") a numeric with direction of wind data
list("speed") a numeric with speed of wind data
#### Details 
 
This data set is the result of:
library(lubridate) dt <- seq(ymd_h(paste(2015,1,3,00, sep="-")),
wind.series <- wind.dl_2(dt, 164, 179, -48, -33)
ymd_h(paste(2015,1,3,21, sep=
Source
http://allthiswasfield.blogspot.com.es/2016/12/rwind-r-package-released.html

#### References 
 
http://oos.soest.hawaii.edu/erddap/info/NCEP_Global_Best/index.html
#### Examples
 ```{r}
data(wind.series)
str(tidy(wind.series))
wind2raster
Wind-data to raster file
#### Description

wind2raster crates a raster stack (gridded) with 2 layers: wind speed and wind direction for an
object of rWind. Latitude and logitude values are used to locate raster file and to create raster using
rasterFromXYZ function from raster package. If the input file is a list of wind data created by
wind.dl, a list of raster stacks will be returned14
wind2raster
Usage
wind2raster(x)
Arguments
x
an "rWind list" obtained by wind.fit
#### Details 
 
WGS84 datum (non-projected) CRS is selected by default to build the raster file.
#### Value

A raster stack or a list of raster stacks representing wind direction and speed.

#### Author(s) 
 
Javier Fernández-López (jflopez@rjb.csic.es)
See Also
wind.dl
#### Examples
 ```{r}
data(wind.data)
# Create raster stack from the downloaded data with wind directon and speed
# layers
wind2raster(wind.data)
