dbh: Diameter at breast height prediction using height and crown diameter
==================================

Prediction of diameter at breast height (DBH) using height and crown diameter and the equations of Jucker et al. (2017).

#### Usage

<pre><code>
dbh(H = NULL, CA = NULL, biome = 0)
</code></pre>

#### Arguments
* ``H`` Tree height in meters.
* ``CA``Crown diameter in meters.
* ``biome`` Integer number indicating the type of biome:

#### biome types

0 = 'Global'
1 = 'Afrotropic-Tropical forests-Angiosperm'
2 = 'Afrotropic-Woodlands and savannas-Angiosperm'
3 = 'Australasia-Temperate mixed forests-Angiosperm'
4 = 'Australasia-Temperate mixed forests-Gymnosperm'
5 = 'Australasia-Woodlands and savannas-Angiosperm'
6 = 'Indo-Malaya-Tropical forests-Angiosperm'
7 = 'Nearctic-Boreal forests-Angiosperm'
8 = 'Nearctic-Boreal forests-Gymnosperm'
9 = 'Nearctic-Temperate coniferous forests-Angiosperm'
10 = 'Nearctic-Temperate coniferous forests-Gymnosperm'
11 = 'Nearctic-Temperate mixed forests-Angiosperm'
12 = 'Nearctic-Temperate mixed forests-Gymnosperm'
13 = 'Nearctic-Woodlands and savannas-Angiosperm'
14 = 'Nearctic-Woodlands and savannas-Gymnosperm'
15 = 'Neotropic-Tropical forests-Angiosperm'
16 = 'Palearctic-Boreal forests-Angiosperm'
17 = 'Palearctic-Boreal forests-Gymnosperm'
18 = 'Palearctic-Temperate coniferous forests-Angiosperm'
19 = 'Palearctic-Temperate coniferous forests-Gymnosperm'
20 = 'Palearctic-Temperate mixed forests-Angiosperm'
21 = 'Palearctic-Temperate mixed forests-Gymnosperm'
22 = 'Palearctic-Tropical forests-Angiosperm'
23 = 'Palearctic-Woodlands and savannas-Angiosperm'
24 = 'Palearctic-Woodlands and savannas-Gymnosperm'

#### Value

The DBH value in centimeters.


#### Examples
```{r}
data(lasData)

## function takes a while to run

#Extraction of the ITCs
se<-itcLiDAR(lasData$X,lasData$Y,lasData$Z,epsg=32632)

summary(se)
```

```{r}
#Computation of the crown diameter from the crown area
se$CD_m<-2*sqrt(se$CA_m2/pi)

#DBH prediction
se$dbh<-NA
se$dbh<-dbh(se$Height_m,se$CD_m,biome=0)

summary(se)
```

#### References
"Allometric equations for integrating remote sensing imagery into forest monitoring programs," Global Change Biology, 23 (1), pp. 177-190, January 2017.

T. Jucker, J. Caspersen, J. Chave, C. Antin, N. Barbier, F. Bongers, M. Dalponte, K. Y. van Ewijk, D. I. Forrester, M. Haeni, S. I. Higgins, R. J. Holdaway, Y. Iida, C. Lorimer, P. L. Marshall, S. Momo, G. R. Moncrieff, P. Ploton, L. Poorter, K. A. 
Rahman, M. Schlund, B. Sonke, F. J. Sterck, A. T. Trugman, V. A. Usoltsev, M. C. Vanderwel, P. Waldner, B. M. M. Wedeux, C. Wirth, H. Woell, M. Woods, W. Xiang, N. E. Zimmermann, and D. A. Coomes, 
