FindTreesCHM : Individual tree detection whitin the LiDAR-derived Canopy Height Model (CHM)
================================================================================
* Detects and computes the location and height of individual trees within the LiDAR-derived Canopy Height Model (CHM). 
* The algorithm implemented in this function is local maximum with a fixed window size.

#### Usage
```{r}
FindTreesCHM(chm,fws,minht)
```
#### Arguments

* ``chm``: A LiDAR-derived Canopy Height Model (CHM) raster file.
* ``fws``: A single dimension (in raster grid cell units) of fixed square window size, e.g. 3, 5, 7 and so on. 
 - Default is 5.
* ``minht``: Height threshold. Detect individual trees above specified height threshold, e.g. 1.37, 2.0, 3.5 m and so on. 
 - Default is 1.37 m.

#### Examples
```{r}

# Importing the LiDAR-derived CHM raster file
data(chm) 
# or set a CHM. e.g. chm<-raster("CHM_stand.asc") 
```
```{r}
# Smoothing CHM
schm<-CHMsmoothing(chm, "mean", 5)

# Setting the fws:
fws<-5 # dimention 5x5

# Setting the specified height above ground for detectionbreak
minht<-8.0

# Getting the individual tree detection list
treeList<-FindTreesCHM(schm, fws, minht)
summary(treeList)
```
```{r}
# Plotting the individual tree location on the CHM
library(raster)
plot(chm, main="LiDAR-derived CHM")
library(sp) 
XY<-SpatialPoints(treeList[,1:2]) # Spatial points
plot(XY, add=TRUE, col="red")        # plotthing tree location

```
