
LASmetrics
LiDAR-derived metrics

#### Description 

Compute LiDAR metrics that describe statistically the Lidar dataset

#### Usage 
<pre><code>
LASmetrics(LASfile, minht, above)
</code></pre>

#### Arguments 

* ``LASfile``: A LAS standard LiDAR data file
* ``minht``: Use only returns above specified height break, e.g. 1.30 m. Default is 1.37 m.
above Compute covers metrics using specified height break, e.g. 2.5 m. Default is 2
m.

#### Examples 
 ```{r} 

#=======================================================================#
# Example 01: Computing LiDAR metrics for a single LAS file
#=======================================================================#
# Import the LAS data file
LASfile <- system.file("extdata", "LASexample1.las", package="rLiDAR")
# Set the minht and above parameters
minht<-1.37 # meters or feet
above<-2.00 # meters or feet
# LiDAR metrics computation
LiDARmetrics<-LASmetrics(LASfile, minht, above)
```

```{r}
#==========================================================================#
# Example 02: Computing Lidar metrics for multiple LAS files within a folder
#==========================================================================#
# Set folder where LAS source files reside
folder=dirname(LASfile)
# Get list of LAS files residing in the folder
LASlist <- list.files(folder, pattern="*.las", full.names=TRUE)
# Set the "minht" and "above" parameters
minht<-1.37 # meters or feet
above<-2.00 # meters or feet
# Creat an empty dataframe in whic to store the LiDAR metrics
getMetrics<-data.frame()
# Set a loop to compute the LiDAR metrics
for ( i in LASlist) {
getMetrics<-rbind(getMetrics, LASmetrics(i, minht, above))}
# Table of the Lidar metrics
LiDARmetrics<-cbind(Files=c(basename(LASlist)), getMetrics)
head(LiDARmetrics)
```

#### Value 

Returns A matrix with the LiDAR-derived vegetation height and canopy cover metrics (see cloud-
metrics, in McGaughey, 2014)

#### Author(s)
Carlos Alberto Silva

#### See Also
McGaughey, R. 2014. FUSION/LDV: Software for lidar data analysis and visualization. Version
3.41. Seattle, WA: U.S. Department of Agriculture, Forest Service, Pacific Northwest Research
Station.

#### List of the LiDAR-derived metrics:
* .... Total all return count
* .... Total first return count
* .... Total all return count above minht
* .... Return 1 count above minht
* .... Return 2 count above minht
* .... Return 3 count above minht
* .... Return 5 count above minht
* .... Return 6 count above minht
* .... Return 7 count above minht
* .... Return 8 count above minht
* .... Return 9 count above minht
* .... HMIN - Maximum Height
* .... HMAX - Maximum Height
* .... HMEAN - Mean height
* .... HMOD - Modal height
* .... HMEDIAN - Median height
* .... HSD - Standard deviation of heights
* .... HVAR - Variance of heights
* .... HCV - Coefficient of variation of heights
* .... HKUR - Kurtosis of Heights
* .... HSKE - Skewness of Heights
* .... H01TH - 01th percentile of height
* .... H05TH - 05th percentile of height
* .... H10TH - 10th percentile of height
* .... H15TH - 15th percentile of height
* .... H20TH - 20th percentile of height
* .... H25TH - 25th percentile of height
* .... H30TH - 30th percentile of height
* .... H35TH - 35th percentile of height
* .... H40TH - 40th percentile of height
* .... H45TH - 45th percentile of height
* .... H50TH - 50th percentile of height
* .... H55TH - 55th percentile of height
* .... H60TH - 60th percentile of height
* .... H65TH - 65th percentile of height
* .... H70TH - 70th percentile of height
* .... H75TH - 75th percentile of height
* .... H80TH - 80th percentile of height
* .... H90TH - 90th percentile of height
* .... H95TH - 95th percentile of height
* .... H99TH - 99th percentile of height
* .... CRR - Canopy relief ratio
* .... IMIN - Minimum intensity
* .... IMAX - Maximum intensity
* .... IMEAN - Mean intensity
* .... IMOD - Modal intensity
* .... IMEDIAN - Median intensity
* .... ISD - Standard deviation of intensities
* .... IVAR - Variance of heights
* .... ICV - Coefficient of variation of intensities
* .... IKUR - Kurtosis of intensities
* .... ISKE - Skewness of intensities
* .... I01TH - 1th percentile of intensity
* .... I05TH - 5th percentile of intensityLASmetrics
* .... I10TH - 10th percentile of intensity
* .... I15TH - 15th percentile of intensity
* .... I20TH - 20th percentile of intensity
* .... I25TH - 25th percentile of intensity
* .... I30TH - 30th percentile of intensity
* .... I35TH - 35th percentile of intensity
* .... I40TH - 40th percentile of intensity
* .... I45TH - 45th percentile of intensity
* .... I50TH - 50th percentile of intensity
* .... I55TH - 55th percentile of intensity
* .... I60TH - 60th percentile of intensity
* .... I65TH - 65th percentile of intensity
* .... I70TH - 70th percentile of intensity
* .... I75TH - 75th percentile of intensity
* .... I80TH - 80th percentile of intensity
* .... I90TH - 90th percentile of intensity
* .... I95TH - 95th percentile of intensity
* .... I99TH - 99th percentile of intensity
* .... Pentage first returns above above
* .... Percentage all returns above above
* .... (All returns above above / Total first returns)*100
* .... First returns above above
* .... All returns above above
* .... Percentage first returns above mean
* .... Percentage first returns above mode
* .... Percentage all returns above mean
* .... Percentage all returns above mode
* .... (All returns above mean / Total first returns)*100
* .... (All returns above mode / Total first returns)* 100
* .... First returns above mean"
* .... First returns above mode
* .... All returns above mean
* .... All returns above mode


