## grid_catalog

Apply a grid function over a catalog

#### Description 

* This function applies over an entire catalog any user-defined function that returns a lasmetrics object. 
* Used internaly by ``grid_metrics``, ``grid_terrain``, ``grid_canopy`` and other ``grid_...`` functions when
the input is a LAScatalog, it ensures continuous rasterization of the dataset and performs pre- and post-processes. 
* This function can be seen as a straightforward ’grid-specific’ version of ``catalog_apply``, which is even more generic.

#### Usage
<pre><code>
grid_catalog(catalog, grid_func, res, select = "*", filter = "",
start = c(0, 0), ...)
</code>></pre>

#### Arguments 

* ``catalog``: A LAScatalog
* ``grid_func``: A function that returns a lasmetrics object. This function must follow a specific template (see Details and Examples) 
* ``res``: numeric. Resolution of the grid
* ``select``: character. The ’select’ parameter from ``readLAS``.
* ``filter``: character. The ’filter’ parameter from ``readLAS``.
* ``start``: numeric. The ’start’ parameter from ``grid_metrics``
* ``...`` Any other parameter required by grid_func

#### Details 

* The user-defined function ``grid_func`` must respect a template. Like in ``grid_metrics``, grid_terrain or
grid_canopy, the user-defined function must have a parameter called x that will receive a LAS object
and a parameter res that will receive the resolution of the grid. The parameter start is optional.

#### Value 

* Returns a data.table containing the metrics for each cell. 
* The table has the class "lasmetrics" enabling easy plotting.

#### Examples   
```{r}
# This example computes the mean elevation of points above 5 m over an entire
# catalog, after removing all points in lakes into a shapefile.
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
shapefile_dir <- system.file("extdata", package = "lidR")2
```
```{r}
ctg = catalog(LASfile)
tiling_size(ctg) <- 160
lakes = rgdal::readOGR(shapefile_dir, "lake_polygons_UTM17")
my_``grid_metrics`` = function(x, res, spdf)
{
lasclassify(x, spdf, "inpoly")
x = lasfilter(x, !inpoly)
``grid_metrics``(x, mean(Z), res)
}
mean = grid_catalog(ctg, my_``grid_metrics``, 20,
select = "xyz", filter = "-drop_z_below 5",
spdf = lakes)
```
