## ``grid_metrics``
Rasterize the space and compute metrics for each cell

#### Description 
* Computes a series of user-defined descriptive statistics for a LiDAR dataset within each pixel of
a raster. 
* Output is a data.table in which each line is a pixel (single grid cell), and each column
is a metric.
* Works both with LAS or catalog objects. ``grid_metrics`` is similar to lasmetrics or
``grid_hexametrics`` except it computes metrics within each cell in a predefined grid. 
* The grid cell coordinates are pre-determined for a given resolution.

#### Usage
<pre><code>
grid_metrics(x, func, res = 20, start = c(0, 0), 
  splitlines = FALSE,
  filter = "")
<code><pre>

#### Arguments 

x
func
res
start
splitlines
filter
An object of class LAS or a catalog (see section "Use with a LAScatalog")
the function to be applied to each cell (see section "Parameter func")
numeric. The size of the cells. Default 20.
vector x and y coordinates for the reference raster. Default is (0,0) (see section
"Parameter start").
logical. If TRUE the algorithm will compute the metrics for each flightline
individually. It returns the same cells several times in overlap.
character. Streaming filter while reading the files (see ``readLAS``). If the input
is a LAScatalog the function ``readLAS`` is called internally. The user cannot
manipulate the lidar data directly but can use streaming filters instead.

#### Details 

* ``grid_metrics`` is similar to lasmetrics or ``grid_hexametrics`` except it computes metrics within each
cell in a predefined grid. 
* The grid cell coordinates are pre-determined for a given resolution, so
the algorithm will always provide the same coordinates independently of the dataset. When start =
(0,0) and res = 20 ``grid_metrics`` will produce the following raster centers: (10,10), (10,30), (30,10)
etc.. When start = (-10, -10) and res = 20 ``grid_metrics`` will produce the following raster centers:
(0,0), (0,20), (20,0) etc.. * In Quebec (Canada) the reference is (-831600, 117980) in the NAD83
coordinate system.

#### Value 

Returns a data.table containing the metrics for each cell. The table has the class "lasmetrics"
enabling easy plotting.
Parameter func
The function to be applied to each cell is a classical function (see Examples) that returns a labelled
list of metrics. The following existing functions allow the user to compute some metrics:
•
•
•
•
stdmetrics
entropy
VCI
LAD
Users must write their own functions to create metrics. ``grid_metrics`` will dispatch the LiDAR
data for each cell in the user’s function. The user writes their function without considering grid
cells, only a point cloud (see example).
Parameter start
The algorithm will always provide the same coordinates independently of the dataset. When start =
(0,0) and res = 20 ``grid_metrics`` will produce the following raster centers: (10,10), (10,30), (30,10)
etc.. When start = (-10, -10) and res = 20 ``grid_metrics`` will produce the following raster centers:
(0,0), (0,20), (20,0) etc.. In Quebec (Canada) reference is (-831600, 117980) in the NAD83 coordi-
nate system.
####  Use with a LAScatalog
When the parameter x is a LAScatalog the function processes the entire dataset in a continuous way
using a multicore process. The user can modify the processing options using the available options.
lidR supports .lax files. Computation speed will be significantly improved with a spatial index.

#### Examples   
```{r}
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
lidar = ``readLAS``(LASfile)

# Canopy surface model with 4 m^2 cells
metrics = ``grid_metrics``(lidar, max(Z), 2)
plot(metrics)
```
```{r}
# Mean height with 400 m^2 cells
metrics = ``grid_metrics``(lidar, mean(Z), 20)
plot(metrics)
```

```{r}
# Define your own new metrics
myMetrics = function(z, i)
{
metrics = list(
zwimean = sum(z*i)/sum(i), # Mean elevation weighted by intensities
zimean = mean(z*i),
# Mean products of z by intensity
zsqmean = sqrt(mean(z^2)) # Quadratic mean
)
}
return(metrics)
metrics = ``grid_metrics``(lidar, myMetrics(Z, Intensity))
plot(metrics)
plot(metrics, "zwimean")
plot(metrics, "zimean")
plot(metrics, "zsqmean")
#etc.
```
