##``grid_metrics3d``

Voxelize the space and compute metrics for each voxel

#### Description 

Voxelize the cloud of points and compute a series of descriptive statistics for each voxel.

#### Usage
<pre><code>g
rid_metrics3d``(.las, func, res = 1, debug = FALSE)
</code></pre>

#### Arguments 
* .las An object of class LAS
* func the function to be apply to each voxel.
* ``res``: numeric. The size of the voxels
* debug logical. If you encounter a non trivial error try debug = TRUE.

#### Details 

Voxelize creates a 3D matrix of voxels with a given resolution. It creates a voxel from the cloud of
points if there is at least one point in the voxel. For each voxel the function allows computation of
one or several derived metrics in the same way as the ``grid_metrics`` functions. Basically there are no
predefined metrics. Users must write their own function to create metrics. Voxelize will dispatch the
LiDAR data for each voxel in the user’s function. The user writes their function without considering
voxels, only a cloud of points (see example).

#### Value 

It returns a data.table containing the metrics for each voxel. The table has the class lasmetrics3d
enabling easier plotting.

#### Examples   
```{r}
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
lidar = ``readLAS``(LASfile)
# Cloud of points is voxelized with a 3-meter resolution and in each voxel
# the number of points is computed.
``grid_metrics3d``(lidar, length(Z), 3)
# Cloud of points is voxelized with a 3-meter resolution and in each voxel
# the mean scan angle of points is computed.
``grid_metrics3d``(lidar, mean(ScanAngle), 3)
## Not run:
```
```{r}
# Define your own metric function
myMetrics = function(i, angle)
{
ret = list(
npoints = length(i),
angle
= mean(angle),
imean
= mean(i)
)
}
return(ret)30
grid_terrain
voxels = ``grid_metrics3d``(lidar, myMetrics(Intensity, ScanAngle), 3)
plot(voxels, color = "angle")
plot(voxels, color = "imean")
#etc.
## End(Not run)

```
