## grid_density

Map the pulse or point density

#### Description 
* Creates a map of the point density. 
* If a "``pulseID``" field is found, return also a map of the pulse density.

#### Usage
<pre><code>
grid_density(x, res = 4, filter = "")
</code></pre>

#### Arguments 

* ``x`` An object of class LAS or a catalog (see section "Use with a LAScatalog")
* ``res``: numeric. The size of a grid cell in LiDAR data coordinates units. 
 - Default is 4 = 16 square meters.
* filter character. Streaming filter while reading the files (see ``readLAS``). 
 - If ``x`` is a LAScatalog the function ``readLAS`` is called internally. 
 - The user cannot manipulate the lidar data directly but can use streaming filters instead.

#### Value 

* Returns a data.table of class lasmetrics which enables easier plotting and RasterLayer casting.

#### Use with a LAScatalog
* When the parameter x is a LAScatalog the function processes the entire dataset in a continuous way
using a multicore process. 
* The user can modify the processing options using the available options. 
* ***lidR*** support ``.lax`` files. 
* Computation speed will be significantly improved with a spatial index.`

#### Examples   
```{r}
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
lidar = ``readLAS``(LASfile)
d = grid_density(lidar, 5)
plot(d)
```

```{r}
d = grid_density(lidar, 10)
plot(d)
```
