

## ````grid_hexametrics````
Compute metrics for hexagonal cells

#### Description 

Computes a series of descriptive statistics for a LiDAR dataset within hexagonal cells from a hexag-
onal grid pattern. This function is identical to ``grid_metrics`` or ``grid_metrics``3d or tree_metrics but
with hexagonal cells instead of classical square pixels. Please refer to ``grid_metrics`` for more infor-
mation.

####  Usage
<pre><code>
``grid_hexametrics``(.las, func, res = 20, splitlines = FALSE, debug = FALSE)
</code></pre>

#### Arguments 

* ``.las``: An object of class LAS
* ``func``: the function to be applied to each hexagonal cell
* ``res``: numeric. The inscribed circle radius of a hexagon. Default = 20.
* ``splitlines``: logical. 
- If TRUE the algorithm will compute the metrics for each flightline individually. 
- It returns the same cells several times in overlaps.
* ``debug logical``:. If you encounter a non trivial error try debug = TRUE.

#### Value 

* It returns a data.table containing the metrics for each hexagonal cell. 
* The table has the clas "lashexametrics" enabling easy plotting.

#### Examples   
```{r}
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
lidar = ``readLAS``(LASfile)
# Maximum elevation with a resolution of 4 m
hm = ``grid_hexametrics``(lidar, max(Z), 4)
plot(hm)
```
```{r}
# Mean height with a resolution of 20 m
hm = ``grid_hexametrics``(lidar, mean(Z))
plot(hm)
```
```{r}
# Define your own new metrics
myMetrics = function(z, i)
{
metrics = list(
zwimean = sum(z*i)/sum(i), # Mean elevation weighted by intensities
zimean = mean(z*i),
# Mean products of z by intensity
zsqmean = sqrt(mean(z^2)) # Quadratic mean
)
}
return(metrics)
metrics = ``grid_hexametrics``(lidar, myMetrics(Z, Intensity), 10)
plot(metrics, "zwimean")
plot(metrics, "zimean")
plot(metrics, "zsqmean")
#etc.
```
