## grid_canopy
Canopy surface model

#### Description 

Creates a canopy surface model using a LiDAR point cloud. For each pixel the function returns
the highest point found (point-to-raster). This basic method could be improved by replacing each
LiDAR return with a small disc. An interpolation for empty pixels is also available.

### Usage
<pre><code>
grid_canopy(x, res = 2, subcircle = 0, na.fill = "none", ...,
filter = "")
</code></pre>
#### Arguments 

* ``x`` An object of class LAS or a catalog (see section "Use with a LAScatalog")
* ``res``: numeric. The size of a grid cell in LiDAR data coordinates units. Default is 2
meters i.e. 4 square meters.
subcircle numeric. radius of the circles. To obtain fewer empty pixels the algorithm can
replace each return with a circle composed of 8 points (see Details).
* ``na.fill``: character. name of the algorithm used to interpolate the data and fill the empty
pixels. Can be "knnidw", "delaunay" or "kriging" (see 
#### Details 
).
... extra parameters for the algorithm used to interpolate the empty pixels (see de-
tails)
filter character. Streaming filter while reading the files (see ``readLAS``). If x is a LAScatalog
the function ``readLAS`` is called internally. The user cannot manipulate the lidar
data directly but can use streaming filters instead.

#### Details 

The algorithm relies on a point-to-raster approach. For each pixel the elevation of the highest point
is found and attributed to this pixel. This method implies that the resulting surface model can con-
tain empty pixels. Those ’holes’ can be filled by interpolation. Internally, the interpolation is based
on the same method used in the function grid_terrain. Therefore the documentation for grid_terrain
is also applicable to this function (see also Examples).

The ’subcircle’ tweak replaces each point with 8 points around the original one. This allows for
virtual ’emulation’ of the fact that a lidar point is not a point as such, but more realistically a disc.
This tweak densifies the point cloud and the resulting canopy model is smoother and contains fewer
’pits’ and empty pixels.

#### Value 

Returns a data.table of class lasmetrics, which enables easier plotting and RasterLayer casting.

### Use with a LAScatalog
When the parameter x is a LAScatalog the function processes the entire dataset in a continuous way
using a multicore process. The user can modify the processing options using the available options.
lidR supports .lax files. Computation speed will be significantly improved with a spatial index.

#### Examples   
```{r}
LASfile <- system.file("extdata", "Megaplot.laz", package="lidR")
lidar = ``readLAS``(LASfile)
# Local maximum algorithm with a resolution of 2 meters
chm = grid_canopy(lidar, 2)
plot(chm)
```
```{r}
# Local maximum algorithm with a resolution of 1 meter replacing each
# point by a 20 cm radius circle of 8 points
chm = grid_canopy(lidar, 1, 0.2)
plot(chm)
```
```{r}
# Local maximum algorithm with a resolution of 1 meter replacing each
# point by a 10 cm radius circle of 8 points and interpolating the empty
# pixels using the 3-nearest neighbours and an inverse-distance weighting.
chm = grid_canopy (lidar, 1, subcircle = 0.1, na.fill = "knnidw", k = 3, p = 2)
plot(chm)
## Not run:
chm = grid_canopy(lidar, 1, na.fill = "knnidw", k = 3)
plot(chm)
chm = grid_canopy(lidar, 1, subcircle = 0.1, na.fill = "delaunay")
plot(chm)
```
