---
title: "Forest Inventory with R"
author: "KevinOBrien"
date: "3 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestinventory)
```
## confint
Calculates Confidence Intervals for Global and Small-Area Estimations

#### Description
Calculates Confidence Intervals for Global and Small-Area Estimations
Usage
<pre><code>
## S3 method for class 'onephase'
confint(object, parm, level = 0.95,
adjust.method = "none", ...)
## S3 method for class 'twophase'
confint(object, parm, level = 0.95,
adjust.method = "none", ...)
## S3 method for class 'threephase'
confint(object, parm, level = 0.95,
adjust.method = "none", ...)
</code></pre>

#### Arguments
* ``object`` object of class onephase, twophase or threephase, containing estimation results of the respective estimation method.
* parm ignored.
* ``level`` the confidence level required.
* ``adjust.method`` correction method to obtain simultaneous confidence intervals for a set of estimates (thus restricted to objects of class "onephase", c("smallarea", "twophase")
and c("smallarea", "threephase")). 
* .... Available correction methods are c("none","bonferroni").
Defaults to "none".
* ... additional arguments, so far ignored.

#### Details
Depending on the estimation method specified, confint() computes confidence intervals as fol-
lows:

#### onephase:
Two-sided confidence intervals are computed based on the t-distribution with n2 - 1 degrees of
freedom, where n2 is the number of terrestrial data in the respective inventory domain.

#### twophase:
* The calculation of the two-sided confidence intervals for global twophase estimates (objects of class
global) are calculated based on the quantiles of the t-distribution with n2 - p degrees of freedom,
where p is the number of parameters used in the regression model, and n2 is the number of terrestrial
observations (i.e. local densities) in the inventory domain.
* The calculation of the two-sided confidence intervals for smallarea twophase estimates (objects of
class smallarea) are calculated based on the quantiles of the t-distribution with n2G - 1 degrees of
freedom, where n2G is the number of terrestrial observations (i.e. local densities) in the smallarea.

#### threephase:
* The calculation of the two-sided confidence intervals for global threephase estimates (objects of
class global) are calculated based on the quantiles of the t-distribution with n2 - p degrees of
freedom, where p is the number of parameters used in the full regression model, and n2 is the
number of terrestrial observations (i.e. local densities) in the inventory domain (note: in notation
used here n0, n1 and n2 correspond to the zero, first and second phase sample sizes respectively).
* The calculation of the two-sided confidence intervals for smallarea theephase estimates (objects of
class smallarea) are calculated based on the quantiles of the t-distribution with n2G - 1 degrees of
freedom, where n2G is the number of terrestrial observations (i.e. local densities) in the smallarea.

#### Value
``confint`` returns a list of the following 3 components:

* ci a data.frame containing the columns:
* ... area the domain, i.e. small area
* ... ci_lower_ext the lower confidence limit based on the external variance
* ... ci_upper_ext the upper confidence limit based on the external variance
* ... ci_lower_g the lower confidence limit based on the g-weight variance
* ... ci_upper_g the upper confidence limit based on the g-weight variance
* level the applied confidence level
* adjust.method the adjustment method applied to retrieve simultaneous confidence intervals

####  Note
* In the special case of synthetic smallarea estimations, the two-sided confidence intervals are calculated based on the quantiles of the t-distribution with n2 - p degrees of freedom, i.e. based on the global sample size.
* The confidence intervals for synthetic smallarea estimations do not account for the potential bias
of a linear model that was fit in a large forest area and applied to a small area. Thus, the coverage
rates for confidence intervals produced by synthetic estimators may be less than the nominal level
of confidence.
* In case of cluster-sampling, n2G is the number of terrestrial clusters (a cluster constitutes the sample
unit). This is automatically considered by confint.
* The adjustment methods passed to adjust.method are designed to achieve simultaneous confidence intervals by correcting the confidence level given by level. The use of this option is recommended if a set of estimates contained in a onephase- or smallarea-object should be compared by
their confidence intervals. It ensures that the percentage of confidence intervals containing the true
value will correspond to the nominal confidence level.


 
#### Examples 
```{r}
## Calculate twophase estimations by extended pseudosynthetic estimator
# for 4 small areas ("A", "B", "C", "D") using the grisons-dataset:
sae.est <- twophase(formula = tvol ~ mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea",
areas = c("A", "B","C", "D"),
unbiased = TRUE))

```

```{r}
## calculate 95%-confidence intervals for each small area:
confint(sae.est)
```

```{r}
## calculate simultaneous 95%-confidence intervals using 'bonferroni'-method:
confint(sae.est, adjust.method = "bonferroni")
```

#### References
* Mandallaz, D. (2013). Design-based properties of some small-area estimators in forest inventory
with two-phase sampling. Canadian Journal of Forest Research, 43(5), 441-449.
* Mandallaz, D., Breschan, J., & Hill, A. (2013). New regression estimators in forest inventories with
two-phase sampling and partially exhaustive information: a design-based monte carlo approach
with applications to small-area estimation. Canadian Journal of Forest Research, 43(11), 1023-
1031.
* Mandallaz, D. (2013). A three-phase sampling extension of the generalized regression estimator
with partially exhaustive information. Canadian Journal of Forest Research, 44(4), 383-388.
Benjamini, Y., and Hochberg, Y. (1995). Controlling the false discovery rate: a practical and
powerful approach to multiple testing. Journal of the Royal Statistical Society Series B 57, 289-
300.
