---
title: "Forest Inventory with R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(forestinventory)
```


## estTable

estTable

#### Description
estTable can be used to compare the results of onephase to multiphase estimations (twophase, threephase). It restructures the estimation results into a table that can be used to plot the estimation results and provides the basis for further analysis.

#### Usage
<pre><code>
estTable(est.list, sae = FALSE, add.ci = TRUE, vartypes = c("variance",
"ext_variance", "g_variance"))
</code></pre>

#### Arguments
* ``est.list`` a list object containing at least one multiphase estimation object created by the twophase or threephase function and the respective onephase estimation object.
* ``sae`` an object of type logical. Has to be set to TRUE if results of small area estimations are passed to estTable. Defaults to FALSE.
* ``add.ci`` logical: Should confidence intervals be added? Defaults to TRUE.
* ``vartypes`` Specifiying the variances that should be included in the estimation table. Has to be specified as a character vector. The full set contains "variance", "ext_variance" and "g_variance".


#### Value
estTable returns a list of the following components:

* ``area``: in case of small area estimations: the name of the small area
* ``estimate``: the point estimates
* ``vartype``: the type of variance
* ``variance``: the variance values
* ``std``: the standard errors (square root of variance values)
* ``error``: the estimation errors defined as the ratio between standard error and point estimate
* ``domain``: indicating if current row belongs to a smallarea or global estimation
* ``estimator``: the estimator that that was applied
* ``method``: the estimation method that was applied
* ``n2``: terrestrial sample size in entire inventory area
* ``n1``: first phase sample size in entire inventory area
* ``n0``: in case of threephase estimations: zero phase sample size in entire inventory area
* ``n2G``: terrestrial sample size in small area6
* ``n1G``: first phase sample size in small area
* ``n0G``: in case of threephase estimations: zero phase sample size in small area
* ``r.squared``: coefficient of determination of regression model
* ``r.squared_reduced``: in case of threephase estimations: coefficient of determination of reduced regression model
* ``r.squared_full``: in case of threephase estimations: coefficient of determination of full regression model
* ``ci_lower``: if add.ci=TRUE: lower confidence limit
* ``ci_upper``: if add.ci=TRUE: upper confidence limit

#### Note
An estimation object of class onephase as input is mandatory


#### Examples 
```{r}
## run onephase estimation:
op.a <- onephase(formula = tvol~1,
data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D")))
```
```{r}
## run small area twophase estimation:
sae.2p.est <- twophase(formula = tvol ~ mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B","C", "D"),
unbiased = TRUE))
```
```{r}
summary(sae.2p.est)
```

```{r}
## run small area threephase estimation:
sae.3p.est <- threephase(formula.s0 = tvol ~ mean,
formula.s1 = tvol ~ mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area=list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = TRUE))
```

```{r}
summary(sae.3p.est)
```


```{r}
## create estimation table with confidence intervals:
sae.table<- estTable(est.list = list(op.a, sae.2p.est, sae.3p.est), add.ci=TRUE,
sae = TRUE, vartypes = c("variance", "g_variance", "ext_variance"))
sae.table.df<- as.data.frame(sae.table)
```
