threephase
threephase

#### Description
threephase is used to calculate estimations based on triple sampling under the model-assisted
Monte Carlo approach. A zero phase of auxiliary information (e.g. taken from remote sensing
data) is used to generate model predictions based on multiple linear regression using the method of
ordinary least squares. A subsample of the zero phase comprises further auxiliary information that
produces another set of model predictions. A further subsample produces a second phase based on
terrestrial observations (i.e. the local densities of the ground truth) and is used to correct for bias
in the design-based sense. The estimation method is available for simple and cluster sampling and
includes the special case where the first phase is based on an exhaustive sample (i.e. a census).
Small-area applications are supported for synthetic estimation as well as two varieties of bias-
corrected estimators: the traditional small-area estimator and an asymptotically equivalent version
derived under * Mandallaz’s extended model approach.

### Usage
<pre><code>
threephase(formula.s0, formula.s1, data, phase_id, cluster = NA,
small_area = list(sa.col = NA, areas = NA, unbiased = TRUE),
boundary_weights = NA, exhaustive = NA, progressbar = FALSE,
psmall = FALSE)
</code></pre>

### Arguments
* ``formula.s0``: an object of class "formula" as would be used in the function lm that contains a
reduced set of auxiliary variables available for all zero phase plots
* ``formula.s1``: an object of class "formula" as would be used in the function lm that contains
the predictors from formula.s0 as well as further ancilliary predictors available
for all first phase plots (i.e. ``formula.s0`` is nested in ``formula.s1``)
* ``data``: a data frame containing all variables contained in formula and a column indexing phase membership. 
 - Additional columns designating small-area membership, cluster ID and boundary weights should also be contained in the data
frame if they are requested in the function.
* ``phase_id``: an object of class "list" containing three elements:
* ``phase.col``: the column name in data that specifies the phase membership
of each observation
* ``s1.id``: the indicator identifying the "second phase only" plots for that col-
umn (must be of type "numeric")
*  ``terrgrid.id``: the indicator identifying the terrestrial (a.k.a. "ground truth")
phase for that column (must be of type "numeric")
* ``cluster`` (Optional) Specifies the column name in data containing the cluster ID. Only
used in case of cluster sampling.
* ``small_area``: (Optional) a list that if containing three elements:
* ``sa.col``: the column name in data containing domain identification
* ``areas``: vector of desired small-area domain identifiers
* ``unbiased``: an object of type "logical" that when FALSE designates that
the estimator is allowed to be biased (i.e. the synthetic estimator) and when TRUE forces it to be design-unbiased. See Details.
Note: If small_area is left unchanged then twophase defaults to global estimation.
* boundary_weights: (Optional) Specifies the column name in data containing the weights for bound-
ary adjustment. See Details.
* exhaustive (Optional) For global estimation, a vector of true auxiliary means corresponding
to an exhaustive first phase. The vector must be input in the same order that lm processes a formula object and include the intercept term. For small area estimation, exhaustive is a data.frame containing column names (colnames)
for every variable appearing in the parameter formula including the variable
"Intercept".Rownames (row.names) have to be used and must correspond to the
names of the small areas. See Details.
* progressbar (Optional) an object a type "logical" that when TRUE prints the progress of
the calculation in the console (recommended for large amount of small areas).
* Defaults to FALSE.
psmall (Optional) an object a type "logical" used for small area estimations that only
works when unbiased in the parameter small_area is set to TRUE. 

#### Details
* s1.id identifies "second phase only" plots because the terrestrial phase is known to be part of the
second phase by the construction of the subsampling.
* If estimations for multiple small-area domains should be computed, the domains have to be defined within a character vector using c(). Using small_area(..., unbiased=FALSE) calculates design-based estimates with the synthetic estimator and may be design-biased if the model is biased in that small area. The default, small_area(..., unbiased=TRUE), allows for a residual
correction by one of two asymptotically equivalent methods to create design-unbiased estimates:
*  Mandallaz’s extended model approach calculates the residual correction by extending the
model formula with an indicator variable in the small area. It is the default method ``psmall=FALSE``.
*  the traditional small area estimator calculates the residual correction by taking the synthetic
estimator and adding the mean residual observed in the small area. It is activated when ``psmall=TRUE``.
Missing values (NA) in the auxiliary variables (i.e. at least one auxiliary variable cannot be observed
at a* n inventory location) are automatically removed from the dataset before the estimations are
computed. Note that missingness in the auxiliary variables is only allowed if we assume that they
are missing at random, since the unbiasedness of the estimates is based on the sampling design.
The boundary weight adjustment is pertinent for auxiliary information derived from remote sensing
and is equal to the percentage of forested area (e.g. as defined by a forest mask) in the interpretation
area.
* Exhaustive estimation refers to when the true means of certain auxiliary variables are known at an
exhaustive zero phase (i.e. a census). For global estimation, the vector must be input in the same
order that lm processes a formula object including the intercept term whose true mean will always
be one. For small area estimation, exhaustive is a data.frame containing column names for every
variable appearing in the parameter formula including the variable "Intercept". The observations of
the data.frame must represent the true auxiliary means in the same order as was presented in areas
from the parameter small_area. See Examples 

####  Value
threephase returns an object of class "threephase".
An object of class "threephase" returns a list of the following components:
input a list containing the function’s inputs
estimation a data frame containing the following components:
*  area: the domain (only present if argument areas has been used)
*  estimate: the point estimatet
*  ext_variance: the external variance of the point estimate that doesn’t
account for fitting the model from the current inventory
*  g_variance: the internal (g-weight) variance that accounts for fitting the
model from the current inventory
*  n0 the zero phase sample size of plots
*  n1 the first phase sample size of plots
*  n2 the second phase (i.e. terrestrial) sample size of plots
*  n0G the zero phase sample size in the small area
*  n1G the first phase sample size in the small area
*  n2G the second phase (i.e. terrestrial) sample size in the small area
*  r.squared_reduced the R-squared of the linear model based on formula.s0
(i.e. the reduced model)
*  r.squared_full the R-squared of the linear model based on formula.s1
(i.e. the full model)
samplesizes a data.frame summarizing all samplesizes: in case of cluster sampling both,
the number of individual plots and the number of clusters is reported.
coefficients the coefficients of the two linear models:
*  alpha: the reduced model coefficients
*  beta: the full model coefficients
cov_alpha_s2 the design-based covariance matrix of the reduced model coefficients
cov_beta_s2 the design-based covariance matrix of the full model coefficients
Z_bar_1_s0 the estimated auxiliary means of formula.s0 based on the zero phase. If the
zero phase is exhaustive, these are the true auxiliary means specified in the input-
argument exhaustive.
Z1_bar_s1 the estimated auxiliary means of formula.s0 based on the first phase
Z_bar_s1 the estimated auxiliary means of formula.s1 based on the first phase
cov_Z_bar_1_s0 the covariance matrix for Z_bar_1_s0
resid_reduced the reduced model residuals at either the plot level or cluster level depending on
the call
resid_full the full model residuals at either the plot level or cluster level depending on the
call
warn.messages logical indicating if warning messages were issued
#### Note
In the special case of cluster sampling, the reported sample sizes in estimation are the number of
clusters. The samplesize-object also provides the respective number of single plot units for cluster
sampling. The reported r.squared_reduced and r.squared_full describe the model fit of the
applied linear regression models (i.e. on plot-level, not on cluster level).18
threephase

#### References
* Mandallaz, D., Breschan, J., & Hill, A. (2013). New regression estimators in forest inventories with
two-phase sampling and partially exhaustive information: a design-based monte carlo approach
with applications to small-area estimation. Canadian Journal of Forest Research, 43(11), 1023-
1031.
* Mandallaz, D. (2014). A three-phase sampling extension of the generalized regression estimator
with partially exhaustive information. Can. J. For. Res. 44: 383-388
Massey, A. and * Mandallaz, D. and Lanz, A. (2014). Integrating remote sensing and past inventory
data under the new annual design of the Swiss National Forest Inventory using three-phase design-
based regression estimation. Can. J. For. Res. 44(10): 1177-1186
* Mandallaz, D. (2013). Regression estimators in forest inventories with three-phase sampling and
two multivariate components of auxiliary information. ETH Zurich, Department of Environmental
Systems Science,Tech. rep. Available from https://doi.org/10.3929/ethz-a-009990020.

 
#### Examples 
```{r}
## load datasets:
data(grisons)
data(zberg)
## define regression models
formula.s0 <- tvol ~ mean #
formula.s1 <- tvol ~ mean +
formula.clust.s0 <- basal ~
formula.clust.s1 <- basal ~
for simple and cluster sampling:
reduced model:
stddev + max + q75 # full model
stade
stade + couver + melange
```

#### GLOBAL ESTIMATION 
```{r}

# ------------------------------------------------#
# ----------- GLOBAL ESTIMATION ------------------#
#----
## 1) -- Design-based estimation with non-exhaustive auxiliary information
#----
# 1.1) non-cluster-sampling (see eqns. [11], [14] and [16] in * Mandallaz 2014):
summary(threephase(formula.s0, formula.s1, data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id=1, terrgrid.id = 2)))
```

```{r}
# 1.2) cluster-sampling (see eqns. [49] and [50] in * Mandallaz 2013):
summary(threephase(formula.clust.s0, formula.clust.s1, data = zberg,
phase_id = list(phase.col="phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster"))
# 1.3) example for boundary weight adjustment (non-cluster example):
summary(threephase(formula.s0, formula.s1, data = grisons,
phase_id = list(phase.col="phase_id_3p", s1.id = 1, terrgrid.id = 2),threephase
19
boundary_weights = "boundary_weights"))
#----
```

#### Design-based estimation with exhaustive auxiliary information
```{r}
## 2) -- Design-based estimation with exhaustive auxiliary information
#----
# 2.1) non-cluster-sampling (see eqns. [7], [9] and [10] in * Mandallaz 2014):
summary(threephase(formula.s0, formula.s1, data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
exhaustive = c(1,11.39)))
# 2.2) cluster-sampling:
summary(threephase(formula.clust.s0, formula.clust.s1, data = zberg,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster", exhaustive = c(1, 0.10, 0.7, 0.10)))
```

#### Small Area Estimation
```{r}
# ----------------------------------------------------#
# ----------- SMALL AREA ESTIMATION ------------------#
#----
## 1) --
#----
Design-based estimation with non-exhaustive auxiliary information
```

```{r}
# 1.1) * Mandallaz's extended pseudo small area estimator:
summary(threephase(formula.s0,
formula.s1,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area=list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = TRUE)))
summary(threephase(formula.clust.s0,
formula.clust.s1,
data = zberg,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"), unbiased = TRUE)))
```

```{r}
# 1.2) pseudo small area estimator:
summary(threephase(formula.s0,
formula.s1,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = TRUE),
psmall = TRUE))
summary(threephase(formula.clust.s0,
formula.clust.s1,
data=zberg,20
threephase
phase_id=list(phase.col="phase_id_3p", s1.id=1, terrgrid.id=2),
cluster="cluster",
small_area=list(sa.col="ismallold", areas=c("1"), unbiased=TRUE),
psmall = TRUE))
```

```{r}
# 1.3) pseudosynthetic small area estimator:
summary(threephase(formula.s0 = tvol ~ mean,
formula.s1 = tvol ~ mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = FALSE)))
summary(threephase(formula.clust.s0,
formula.clust.s1,
data = zberg,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"), unbiased = FALSE)))
```

```{r}
# Design-based estimation with exhaustive auxiliary information
# true auxiliary mean for variable "mean" taken from * Mandallaz et al. (2013):
truemeans.G <- data.frame(Intercept = rep(1, 4),
mean = c(12.85, 12.21, 9.33, 10.45))
rownames(truemeans.G) <- c("A", "B", "C", "D")
# true auxiliary means taken from * Mandallaz (1991):
truemeans.G.clust <- data.frame(Intercept = 1, stade400 = 0.175, stade500 = 0.429,
stade600 = 0.321)
rownames(truemeans.G.clust) <- c("1")
```

#### Mandallaz's extended small area estimator

```{r}
# 2.1) Mandallaz's extended small area estimator:
summary(threephase(formula.s0,
formula.s1,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = TRUE),
exhaustive = truemeans.G))
summary(threephase(formula.clust.s0,
formula.clust.s1,
data = zberg,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"), unbiased = TRUE),
exhaustive = truemeans.G.clust))
```

```{r}
# 2.2) small area estimator:
summary(threephase(formula.s0,
formula.s1,
data = grisons,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
unbiased = TRUE),
exhaustive = truemeans.G,
psmall = TRUE))
```
```{r}
summary(threephase(formula.clust.s0,
formula.clust.s1,
data = zberg,
phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"), unbiased = TRUE),
exhaustive = truemeans.G.clust,
psmall = TRUE))
```

```{r}
# 2.3) synthetic small area estimator:
summary(threephase(formula.s0,
  formula.s1,
  data = grisons,
  phase_id = list(phase.col="phase_id_3p", s1.id = 1, terrgrid.id = 2),
  small_area = list(sa.col = "smallarea", areas = c("A", "B", "C", "D"),
  unbiased = FALSE),
  exhaustive = truemeans.G))
```
```{r}
summary(threephase(formula.clust.s0,
 formula.clust.s1,
 data = zberg,
 phase_id = list(phase.col = "phase_id_3p", s1.id = 1, terrgrid.id = 2),
 cluster = "cluster",
 small_area = list(sa.col = "ismallold", areas = c("1"), unbiased = FALSE),
 exhaustive = truemeans.G.clust))
```
