


twophase
twophase

#### Description
twophase is used to calculate estimations based on double sampling under the model-assisted Monte
Carlo approach. A first phase of auxiliary information (e.g. taken from remote sensing data) is used
to generate model predictions based on multiple linear regression using the method of ordinary
least squares. A subsample of the first phase comprises the second phase which contains terrestrial22
twophase
observations (i.e. the local densities of the ground truth) that is used to correct for bias in the design-
based sense. The estimation method is available for simple and cluster sampling and includes
the special case where the first phase is based on an exhaustive sample (i.e. a census). Small-
area applications are supported for synthetic estimation as well as two varieties of bias-corrected
estimators: the traditional small-area estimator and an asymptotically equivalent version derived
under * Mandallaz’s extended model approach.

### Usage
twophase(formula, data, phase_id, cluster = NA, small_area = list(sa.col =
NA, areas = NA, unbiased = TRUE), boundary_weights = NA, exhaustive = NA,
progressbar = FALSE, psmall = FALSE)

### Arguments
formula an object of class "formula" as would be used in the function lm
data a data frame containing all variables contained in formula and a column in-
dexing phase membership. Additional columns designating small-area mem-
bership, cluster ID and boundary weights should also be contained in the data
frame if they are requested in the function.
phase_id an object of class "list" containing two elements:
*  phase.col: the column name in data that specifies the phase membership
of each observation
*  terrgrid.id: the indicator identifying the terrestrial (a.k.a. "ground truth")
phase for that column (must be of type "numeric")
cluster (Optional) Specifies the column name in data containing the cluster ID. Only
used in case of cluster sampling.
small_area (Optional) a list that if containing three elements:
*  sa.col: the column name in data containing domain identification
*  areas: vector of desired small-area domain identifiers
*  unbiased: an object of type "logical" that when FALSE designates that
the estimator is allowed to be biased (i.e. the synthetic estimator) and when
TRUE forces it to be design-unbiased. See ’

#### Details.
Note: If small_area is left unchanged then twophase defaults to global esti-
mation.
boundary_weights
(Optional) Specifies the column name in data containing the weights for bound-
ary adjustment. See ’
#### Details’
exhaustive
(Optional) For global estimation, a vector of true auxiliary means corresponding
to an exhaustive first phase. The vector must be input in the same order that
lm processes a formula object and include the intercept term. For small area
estimation, exhaustive is a data.frame containing column names (colnames)
for every variable appearing in the parameter formula including the variable
"Intercept".Rownames (row.names) have to be used and must correspond to the
names of the small areas. See ’
#### Details’.twophase
23
progressbar (Optional) an object a type "logical" that when TRUE prints the progress of
the calculation in the console (recommended for large amount of small areas).
Defaults to FALSE.
psmall (Optional) an object a type "logical" used for small area estimations that only
works when unbiased in the parameter small_area is set to TRUE. See ’De-
tails’.

#### Details
If estimations for multiple small-area domains should be computed, the domains have to be defined
within a character vector using c(). Using small_area(..., unbiased=FALSE) calculates
design-based estimates with the synthetic estimator and may be design-biased if the model is bi-
ased in that small area. The default, small_area(..., unbiased=TRUE), allows for a residual
correction by one of two asympototically equivalent methods to create design-unbiased estimates:
Mandallaz’s extended model approach calculates the residual correction by extending the
model formula with an indicator variable in the small area. It is the default method psmall=FALSE.
the traditional small area estimator calculates the residual correction by taking the synthetic
estimator and adding the mean residual observed in the small area. It is activated when
psmall=TRUE.

Missing values (NA) in the auxiliary variables (i.e. at least one auxiliary variable cannot be observed
at an inventory location) are automatically removed from the dataset before the estimations are
computed. Note that missingness in the auxiliary variables is only allowed if we assume that they
are missing at random, since the unbiasedness of the estimates is based on the sampling design.
The boundary weight adjustment is pertinent for auxiliary information derived from remote sensing
and is equal to the percentage of forested area (e.g. as defined by a forest mask) in the interpretation
area.

Exhaustive estimation refers to when the true means of certain auxiliary variables are known and
an exhaustive first phase (i.e. a census). For global estimation, the vector must be input in the same
order that lm processes a formula object including the intercept term whose true mean will always
be one. For small area estimation, exhaustive is a data.frame containing column names for every
variable appearing in the parameter formula including the variable "Intercept". The observations of
the data.frame must represent the true auxiliary means in the same order as was presented in areas
from the parameter small_area. See Examples 

### Value
twophase returns an object of class "twophase".
An object of class "twophase" returns a list of the following components:
input a list containing the function’s inputs
estimation a data frame containing the following components:
*  area: the domain (only present if argument areas has been used)
*  estimate: the point estimate
*  ext_variance: the external variance of the point estimate that doesn’t
account for fitting the model from the current inventory24
twophase
*  g_variance: the internal (g-weight) variance that accounts for fitting the
model from the current inventory
*  n1 the first phase sample size of plots
*  n2 the second phase (i.e. terrestrial) sample size of plots
*  n1G the first phase sample size in the small area
*  n2G the second phase (i.e. terrestrial) sample size in the small area
*  r.squared the R squared of the linear model
samplesizes a data.frame summarizing all samplesizes: in case of cluster sampling both,
the number of individual plots and the nuber of clusters is reported.
coefficients the linear model coefficients
cov_coef the design-based covariance matrix of the model coefficients
Z_bar_1G the estimated auxiliary means of formula based on the first phase. If the first
phase is exhaustive, these are the true auxiliary means specified in the input-
argument exhaustive.
cov_Z_bar_1G the covariance matrix of Z_bar_1G
Rc_x_hat_G the small-area residuals at either the plot level or cluster level depending on the
call
Rc_x_hat the residuals at either the plot level or cluster level depending on the call
Yx_s2G the local densities in the small area
Mx_s2G the cluster weights in the small area
mean_Rc_x_hat_G
the mean residual (weighted mean in the case of cluster sampling) in the small
area
mean_Rc_x_hat the mean residual (weighted mean in the case of cluster sampling)
warn.messages logical indicating if warning messages were issued

#### Note
In the special case of cluster sampling, the reported sample sizes in estimation are the number of
clusters. The samplesize-object also provides the respective number of single plot units for cluster
sampling. The reported r.squared describe the model fit of the applied linear regression model
(i.e. on plot-level, not on cluster level).

#### References
* Mandallaz, D. (2007). Sampling techniques for forest inventories. Chapter 4. CRC Press.
* Mandallaz, D. (2013). Design-based properties of some small-area estimators in forest inventory
with two-phase sampling. Can. J. For. Res. 43: 441-449
* Mandallaz, D. and Hill, A. and Massey, A. (2016). Design-based properties of some small-area
estimators in forest inventory with two-phase sampling. ETH Zurich, Department of Environmental
Systems Science,Tech. rep. Available from http://e-collection.library.ethz.ch.twophase

 
#### Examples 
```{r}
## load datasets:
data(grisons)
data(zberg)
```

```{r}
# ----------- GLOBAL ESTIMATION ------------------#
#----
## 1) -- Design-based estimation with non-exhaustive auxiliary information
#----
# 1.1) non-cluster-sampling:
summary(twophase(formula = tvol ~mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2)))
```

```{r}
# 1.2) cluster-sampling (see eqns. [57] and [58] in Mandallaz, Hill, Massey 2016):
summary(twophase(formula = basal ~ stade + couver + melange,
data = zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster"))
```

```{r}
# 1.3) example for boundary weight adjustment (non-cluster example):
summary(twophase(formula=tvol ~ mean + stddev + max + q75,
data=grisons,
phase_id=list(phase.col = "phase_id_2p", terrgrid.id = 2),
boundary_weights = "boundary_weights"))
```

```{r}

## 2) -- Design-based estimation with exhaustive auxiliary information
#----
# establish order for vector of true auxiliary means:
colnames(lm(formula = tvol ~ mean + stddev + max + q75, data = grisons, x = TRUE)$x)
true.means <- c(1, 11.39, 8.84, 32.68, 18.03)
# 2.1) non-cluster-sampling:
summary(twophase(formula = tvol ~ mean + stddev + max + q75,
data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
exhaustive = true.means))
# 2.2) cluster-sampling:
summary(twophase(formula = stem ~ stade + couver + melange,
data = zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
exhaustive = c(1, 0.10, 0.7, 0.10, 0.6, 0.8)))
```

```{r}
# ----------------------------------------------------#
# ----------- SMALL AREA ESTIMATION ------------------#
#----
## 1) -- Design-based estimation with non-exhaustive auxiliary information
#----
# 1.1) * Mandallaz's extended pseudo small area estimator (see eqns. [35] and [36] in * Mandallaz 2013):
summary(twophase(formula = tvol ~ mean + stddev + max + q75, data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B","C", "D"),
unbiased = TRUE)))
summary(twophase(formula = basal ~ stade + couver + melange, data=zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallg23", areas = c("2", "3"),
unbiased = TRUE)))
```

```{r}
# 1.2) pseudo small area estimator (see eqns. [25] and [26] in * Mandallaz 2013):
summary(twophase(formula = tvol ~ mean + stddev + max + q75, data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A", "B"),
unbiased = TRUE),
psmall = TRUE))
summary(twophase(formula = basal ~ stade + couver + melange, data=zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallg23", areas = c("2", "3"),
unbiased = TRUE),
psmall = TRUE))
```

```{r}

# 1.3) pseudosynthetic small area estimator (see eqns. [35] and [36] in * Mandallaz 2013):
summary(twophase(formula = tvol ~ mean + stddev + max + q75, data=grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("B", "A"),
unbiased = FALSE)))
summary(twophase(formula = basal ~ stade + couver + melange, data=zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallg23", areas = c("2", "3"),
unbiased = FALSE)))
```

```{r}
#----
## 2) -- Design-based estimation with exhaustive auxiliary information
#----
# establish order for vector of true auxiliary means:twophase
27
colnames(lm(formula = tvol ~ mean + stddev + max + q75, data = grisons, x = TRUE)$x)
colnames(lm(formula = basal ~ stade + couver + melange, data = zberg, x = TRUE)$x)
# true auxiliary means taken from * Mandallaz et al. (2013):
truemeans.G <- data.frame(Intercept = rep(1, 4),
mean = c(12.85, 12.21, 9.33, 10.45),
stddev = c(9.31, 9.47, 7.90, 8.36),
max = c(34.92, 35.36, 28.81, 30.22),
q75 = c(19.77, 19.16, 15.40, 16.91))
rownames(truemeans.G) <- c("A", "B", "C", "D")
# true auxiliary means taken from * Mandallaz (1991):
truemeans.G.clust <- data.frame(Intercept = 1,
stade400 = 0.175,
stade500 = 0.429,
stade600 = 0.321,
couver2 = 0.791,
melange2 = 0.809)
rownames(truemeans.G.clust) <- c("1")
# 2.1) * Mandallaz's extended small area estimator (see eqns. [31] and [33] in * Mandallaz 2013):
summary(twophase(formula = tvol ~ mean + stddev + max + q75, data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col ="smallarea", areas = c("A", "B"),
unbiased = TRUE),
exhaustive = truemeans.G))
summary(twophase(formula = basal ~ stade + couver + melange, data=zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"),
unbiased = TRUE),
exhaustive = truemeans.G.clust))
```

```{r}
# 2.2) small area estimator (see eqns. [20] and [21] in * Mandallaz 2013):
summary(twophase(formula = tvol ~ mean + stddev + max + q75, data = grisons,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area = list(sa.col = "smallarea", areas = c("A"),
unbiased = TRUE),
exhaustive = truemeans.G, psmall = TRUE))
summary(twophase(formula = basal ~ stade + couver + melange, data = zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col ="ismallold", areas = c("1"),
unbiased = TRUE),
psmall = TRUE,
exhaustive = truemeans.G.clust))
```

```{r}
# 2.3) synthetic small area estimator (see eqns. [18] and [19] in * Mandallaz 2013):28
zberg
summary(twophase(formula=tvol ~ mean + stddev + max + q75, data=grisons,
phase_id=list(phase.col = "phase_id_2p", terrgrid.id = 2),
small_area=list(sa.col = "smallarea", areas = c("A", "B"),
unbiased = FALSE),
exhaustive = truemeans.G))
summary(twophase(formula = basal ~ stade + couver + melange, data = zberg,
phase_id = list(phase.col = "phase_id_2p", terrgrid.id = 2),
cluster = "cluster",
small_area = list(sa.col = "ismallold", areas = c("1"),
unbiased = FALSE),
exhaustive = truemeans.G.clust))
```
